---
title: "Analysis"
format: html
---

This document plots the time domain and spectral kurtosis features from the RUL challenge dataset using plotly slide shows. It also saves the slide shows as HTML files in the respective folders.

```{r}

# renv::install("signal")
# renv::install("e1071")
# renv::install("av")
# renv::install("future")
# renv::install("furrr")
# renv::install("plotly")
# renv::install("htmlwidgets")

library(tidyverse)
library(DBI)
library(duckdb)
library(sparklyr)
library(signal)
library(e1071)
library(av)
library(parallel)
library(future)
library(furrr)
library(data.table)
library(plotly)
library(htmlwidgets)
```

Load the time domain and spectral kurtosis features .rds files.


```{r}
time_domain_features <- readRDS(
  "G:\\My Drive\\rao@ualberta.ca 2022-12-08 10 58\\shishir@tamu.edu\\My Drive\\Interesting papers\\Survival Models\\Reliability\\RUL Challenge\\RUL-challenge\\G_1\\channel_1\\time_domain_features.rds"
)
spectral_kurtosis_features <- readRDS(
  "G:\\My Drive\\rao@ualberta.ca 2022-12-08 10 58\\shishir@tamu.edu\\My Drive\\Interesting papers\\Survival Models\\Reliability\\RUL Challenge\\RUL-challenge\\G_1\\channel_1\\sk_summary_features.rds"
)
```

Every column in every element in the time domain features and spectral kurtosis features is a feature. I want to plot this against time. Every list element is the feature value at 2 minute intervals. For example, the first list element is at 2 minutes, the second is at 4 minutes and so on. I want a function that takes in both the lists and plots every feature against time in a plotly slide show. In the slide show, I want an option to play, move ahead 1 step or move back one step. After writing that function, I want a code that loops through all the folders and all the channels by calling that function iteratively. Every plotly slide show should be saved as an html file in the respective folder of the channel.

Here is the function that creates the plotly slide show for the features:


```{r}
create_feature_timeseries_slideshow <- function(
  time_domain_features,
  spectral_kurtosis_features,
  output_file = "feature_timeseries.html",
  time_interval_minutes = 2
) {
  # Convert lists to data frames
  td_df <- bind_rows(time_domain_features, .id = "signal_id")
  sk_df <- bind_rows(spectral_kurtosis_features, .id = "signal_id")

  # Combine both feature sets
  combined_df <- bind_cols(td_df, sk_df |> select(-signal_id))

  # Add time column
  combined_df <- combined_df |>
    mutate(
      signal_id = as.integer(signal_id),
      Time_minutes = signal_id * time_interval_minutes
    )

  # Get all feature names (exclude signal_id and Time_minutes)
  feature_names <- setdiff(names(combined_df), c("signal_id", "Time_minutes"))

  # Reshape to long format for plotting
  plot_data <- combined_df |>
    select(Time_minutes, all_of(feature_names)) |>
    pivot_longer(
      cols = all_of(feature_names),
      names_to = "Feature",
      values_to = "Value"
    )

  # Calculate y-axis range for each feature
  feature_ranges <- plot_data |>
    group_by(Feature) |>
    summarize(
      ymin = min(Value, na.rm = TRUE),
      ymax = max(Value, na.rm = TRUE),
      .groups = "drop"
    ) |>
    mutate(
      # Add 5% padding to y-axis range
      padding = (ymax - ymin) * 0.05,
      ymin = ymin - padding,
      ymax = ymax + padding
    )

  # Create frames manually with proper y-axis ranges
  frames <- lapply(feature_names, function(feat) {
    feat_data <- plot_data |> filter(Feature == feat)
    feat_range <- feature_ranges |> filter(Feature == feat)

    list(
      data = list(
        list(
          x = feat_data$Time_minutes,
          y = feat_data$Value,
          type = "scatter",
          mode = "lines+markers",
          marker = list(size = 6),
          line = list(width = 2)
        )
      ),
      name = feat,
      layout = list(
        yaxis = list(
          range = c(feat_range$ymin, feat_range$ymax),
          title = "Feature Value"
        )
      )
    )
  })

  # Create initial plot with first feature
  first_feature_data <- plot_data |> filter(Feature == feature_names[1])
  first_range <- feature_ranges |> filter(Feature == feature_names[1])

  fig <- plot_ly() |>
    add_trace(
      data = first_feature_data,
      x = ~Time_minutes,
      y = ~Value,
      type = 'scatter',
      mode = 'lines+markers',
      marker = list(size = 6),
      line = list(width = 2)
    ) |>
    layout(
      title = "Feature Evolution Over Time",
      xaxis = list(title = "Time (minutes)"),
      yaxis = list(
        title = "Feature Value",
        range = c(first_range$ymin, first_range$ymax)
      ),
      updatemenus = list(
        list(
          type = "buttons",
          direction = "right",
          x = 0.7,
          y = 1.15,
          buttons = list(
            list(
              label = "Play",
              method = "animate",
              args = list(
                NULL,
                list(
                  frame = list(duration = 500, redraw = TRUE),
                  fromcurrent = TRUE,
                  mode = "immediate",
                  transition = list(duration = 300)
                )
              )
            ),
            list(
              label = "Pause",
              method = "animate",
              args = list(
                list(NULL),
                list(
                  frame = list(duration = 0, redraw = FALSE),
                  mode = "immediate",
                  transition = list(duration = 0)
                )
              )
            )
          )
        )
      ),
      sliders = list(
        list(
          active = 0,
          steps = lapply(seq_along(feature_names), function(i) {
            list(
              label = feature_names[i],
              method = "animate",
              args = list(
                list(feature_names[i]),
                list(
                  mode = "immediate",
                  frame = list(duration = 300, redraw = TRUE),
                  transition = list(duration = 300)
                )
              )
            )
          }),
          currentvalue = list(
            prefix = "Feature: ",
            visible = TRUE,
            xanchor = "center"
          ),
          len = 0.9,
          x = 0.05,
          y = 0,
          pad = list(t = 50, b = 10)
        )
      )
    )

  # Add frames to the figure
  fig$x$frames <- frames

  # Save as HTML
  saveWidget(fig, output_file, selfcontained = TRUE)

  cat("Slideshow saved to:", normalizePath(output_file), "\n")

  return(invisible(fig))
}
```

Test the function with the loaded features.


```{r}
create_feature_timeseries_slideshow(
  time_domain_features,
  spectral_kurtosis_features,
  output_file = "feature_timeseries.html"
)
```

Now, to loop through all the folders and channels, you can use the following code. Make sure to adjust the base directory path as needed.


```{r}
# Define base directory and schemas
base_dir <- "G:\\My Drive\\rao@ualberta.ca 2022-12-08 10 58\\shishir@tamu.edu\\My Drive\\Interesting papers\\Survival Models\\Reliability\\RUL Challenge\\RUL-challenge"

# Define all schemas
train_schemas <- c("G_1", "G_2", "G_3", "G_4", "G_5")
test_schemas <- paste0("G_6_test_", 1:5)
all_schemas <- c(train_schemas, test_schemas)

# Define channels
channels <- c(
  "channel_1",
  "channel_2",
  "channel_3",
  "channel_4",
  "channel_5",
  "channel_6",
  "channel_7",
  "channel_8",
  "channel_9",
  "channel_10",
  "channel_11"
)

# Process all combinations
results_log <- list()

for (schema in all_schemas) {
  cat("\n=== Processing Schema:", schema, "===\n")

  for (channel in channels) {
    folder_path <- file.path(base_dir, schema, channel)

    # Check if folder exists
    if (!dir.exists(folder_path)) {
      cat("Skipping", schema, "/", channel, "- folder not found\n")
      next
    }

    # Define file paths
    td_file <- file.path(folder_path, "time_domain_features.rds")
    sk_file <- file.path(folder_path, "sk_summary_features.rds")

    # Check if both files exist
    if (!file.exists(td_file) || !file.exists(sk_file)) {
      cat("Skipping", schema, "/", channel, "- missing feature files\n")
      next
    }

    cat("Processing:", schema, "/", channel, "\n")

    # Load features
    tryCatch(
      {
        time_domain_features <- readRDS(td_file)
        spectral_kurtosis_features <- readRDS(sk_file)

        # Create output file path
        output_html <- file.path(folder_path, "feature_timeseries.html")

        # Generate slideshow
        create_feature_timeseries_slideshow(
          time_domain_features = time_domain_features,
          spectral_kurtosis_features = spectral_kurtosis_features,
          output_file = output_html,
          time_interval_minutes = 2
        )

        results_log[[length(results_log) + 1]] <- list(
          schema = schema,
          channel = channel,
          status = "success",
          n_signals = length(time_domain_features)
        )

        cat("  ✓ Completed:", channel, "\n")
      },
      error = function(e) {
        cat("  ✗ Error processing", channel, ":", e$message, "\n")
        results_log[[length(results_log) + 1]] <- list(
          schema = schema,
          channel = channel,
          status = "error",
          error = e$message
        )
      }
    )
  }
}

# Convert results log to data frame
results_df <- bind_rows(results_log)

cat("\n=== Processing Complete ===\n")
cat("Total successful:", sum(results_df$status == "success"), "\n")
cat("Total errors:", sum(results_df$status == "error"), "\n")

# Save results log
saveRDS(results_df, file.path(base_dir, "feature_slideshow_results.rds"))
```

Next, I want to do something similar in terms of a plotly slide show, but this time, I want all gearboxes for a particular channel on the same slide show. For example, for channel 1, I want all the gearboxes G_1 to G_5 and G_6_test_1 to G_6_test_5 plotted in the same slide show. The x axis will still be time in minutes, but now, every feature will have 10 lines - one for each gearbox. The y axis will still be the feature value. The slide show should have the same play, move ahead 1 step and move back 1 step options. Every plotly slide show should be saved as an html file in a new folder called "all_gearboxes" inside the base directory.

Function to create the combined gearbox slide show:

```{r}
create_multi_gearbox_slideshow <- function(
  channel_name,
  all_schemas,
  base_dir,
  output_file,
  time_interval_minutes = 2
) {
  # Collect data from all gearboxes for this channel
  all_gearbox_data <- list()

  for (schema in all_schemas) {
    folder_path <- file.path(base_dir, schema, channel_name)

    # Check if folder and files exist
    td_file <- file.path(folder_path, "time_domain_features.rds")
    sk_file <- file.path(folder_path, "sk_summary_features.rds")

    if (
      !dir.exists(folder_path) || !file.exists(td_file) || !file.exists(sk_file)
    ) {
      cat("Skipping", schema, "- missing data\n")
      next
    }

    # Load features
    tryCatch(
      {
        td_features <- readRDS(td_file)
        sk_features <- readRDS(sk_file)

        # Convert to data frames
        td_df <- bind_rows(td_features, .id = "signal_id")
        sk_df <- bind_rows(sk_features, .id = "signal_id")

        # Combine and add metadata
        combined <- bind_cols(td_df, sk_df |> select(-signal_id)) |>
          mutate(
            signal_id = as.integer(signal_id),
            Time_minutes = signal_id * time_interval_minutes,
            Gearbox = schema
          )

        all_gearbox_data[[schema]] <- combined
      },
      error = function(e) {
        cat("Error loading", schema, ":", e$message, "\n")
      }
    )
  }

  # Check if we have data
  if (length(all_gearbox_data) == 0) {
    stop("No data found for channel ", channel_name)
  }

  # Combine all gearbox data
  combined_df <- bind_rows(all_gearbox_data)

  # Get feature names (exclude metadata columns)
  feature_names <- setdiff(
    names(combined_df),
    c("signal_id", "Time_minutes", "Gearbox")
  )

  # Reshape to long format
  plot_data <- combined_df |>
    select(Time_minutes, Gearbox, all_of(feature_names)) |>
    pivot_longer(
      cols = all_of(feature_names),
      names_to = "Feature",
      values_to = "Value"
    )

  # Calculate y-axis range for each feature across all gearboxes
  feature_ranges <- plot_data |>
    group_by(Feature) |>
    summarize(
      ymin = min(Value, na.rm = TRUE),
      ymax = max(Value, na.rm = TRUE),
      .groups = "drop"
    ) |>
    mutate(
      padding = (ymax - ymin) * 0.05,
      ymin = ymin - padding,
      ymax = ymax + padding
    )

  # Create frames for each feature
  frames <- lapply(feature_names, function(feat) {
    feat_data <- plot_data |> filter(Feature == feat)
    feat_range <- feature_ranges |> filter(Feature == feat)

    # Create a trace for each gearbox
    traces <- lapply(unique(feat_data$Gearbox), function(gb) {
      gb_data <- feat_data |> filter(Gearbox == gb)
      list(
        x = gb_data$Time_minutes,
        y = gb_data$Value,
        type = "scatter",
        mode = "lines+markers",
        name = gb,
        marker = list(size = 4),
        line = list(width = 2)
      )
    })

    list(
      data = traces,
      name = feat,
      layout = list(
        yaxis = list(
          range = c(feat_range$ymin, feat_range$ymax),
          title = "Feature Value"
        )
      )
    )
  })

  # Create initial plot with first feature
  first_feature_data <- plot_data |> filter(Feature == feature_names[1])
  first_range <- feature_ranges |> filter(Feature == feature_names[1])

  fig <- plot_ly()

  # Add traces for each gearbox for the first feature
  for (gb in unique(first_feature_data$Gearbox)) {
    gb_data <- first_feature_data |> filter(Gearbox == gb)
    fig <- fig |>
      add_trace(
        data = gb_data,
        x = ~Time_minutes,
        y = ~Value,
        type = 'scatter',
        mode = 'lines+markers',
        name = gb,
        marker = list(size = 4),
        line = list(width = 2)
      )
  }

  # Add layout with controls
  fig <- fig |>
    layout(
      title = paste("Feature Evolution Over Time -", channel_name),
      xaxis = list(title = "Time (minutes)"),
      yaxis = list(
        title = "Feature Value",
        range = c(first_range$ymin, first_range$ymax)
      ),
      updatemenus = list(
        list(
          type = "buttons",
          direction = "right",
          x = 0.7,
          y = 1.15,
          buttons = list(
            list(
              label = "Play",
              method = "animate",
              args = list(
                NULL,
                list(
                  frame = list(duration = 500, redraw = TRUE),
                  fromcurrent = TRUE,
                  mode = "immediate",
                  transition = list(duration = 300)
                )
              )
            ),
            list(
              label = "Pause",
              method = "animate",
              args = list(
                list(NULL),
                list(
                  frame = list(duration = 0, redraw = FALSE),
                  mode = "immediate",
                  transition = list(duration = 0)
                )
              )
            )
          )
        )
      ),
      sliders = list(
        list(
          active = 0,
          steps = lapply(seq_along(feature_names), function(i) {
            list(
              label = feature_names[i],
              method = "animate",
              args = list(
                list(feature_names[i]),
                list(
                  mode = "immediate",
                  frame = list(duration = 300, redraw = TRUE),
                  transition = list(duration = 300)
                )
              )
            )
          }),
          currentvalue = list(
            prefix = "Feature: ",
            visible = TRUE,
            xanchor = "center"
          ),
          len = 0.9,
          x = 0.05,
          y = 0,
          pad = list(t = 50, b = 10)
        )
      )
    )

  # Add frames
  fig$x$frames <- frames

  # Save as HTML
  saveWidget(fig, output_file, selfcontained = TRUE)

  cat("Multi-gearbox slideshow saved to:", normalizePath(output_file), "\n")

  return(invisible(fig))
}
```

Loop through all channels to create the multi-gearbox slide shows:


```{r}
# Create output directory
output_dir <- file.path(base_dir, "all_gearboxes")
dir.create(output_dir, showWarnings = FALSE, recursive = TRUE)

# Process each channel
channel_results <- list()

for (channel in channels) {
  cat("\n=== Processing Channel:", channel, "===\n")

  output_file <- file.path(output_dir, paste0(channel, "_all_gearboxes.html"))

  tryCatch(
    {
      create_multi_gearbox_slideshow(
        channel_name = channel,
        all_schemas = all_schemas,
        base_dir = base_dir,
        output_file = output_file,
        time_interval_minutes = 2
      )

      channel_results[[length(channel_results) + 1]] <- list(
        channel = channel,
        status = "success"
      )

      cat("✓ Completed:", channel, "\n")
    },
    error = function(e) {
      cat("✗ Error processing", channel, ":", e$message, "\n")
      channel_results[[length(channel_results) + 1]] <- list(
        channel = channel,
        status = "error",
        error = e$message
      )
    }
  )
}

# Convert results to data frame
channel_results_df <- bind_rows(channel_results)

cat("\n=== Multi-Gearbox Processing Complete ===\n")
cat("Total successful:", sum(channel_results_df$status == "success"), "\n")
cat("Total errors:", sum(channel_results_df$status == "error"), "\n")

# Save results log
saveRDS(channel_results_df, file.path(output_dir, "multi_gearbox_results.rds"))
```