---
title: "RUL Challenge Create Database"
format: html
---

This file is for the sole purpose of creating a duckdb database of the RUL Challenge data. After loading, I tested whether I was able to connect from R. I was. Success. Nothing else is done here. Once loaded, the database can be queried from other R scripts.

Load libraries into renv.

```{r}

# renv::install("tidyverse")
# renv::install("DBI")
# renv::install("duckdb")
# renv::install("sparklyr")

library(tidyverse)
library(DBI)
library(duckdb)
library(sparklyr)


```


Load data into DuckDB database.

```{r}
# # 1. Define the folder names (your "G" folders)
# g_folders <- paste0("G_", 1:5)

# # 2. Define the CSV file names
# # Use a pattern that matches "channel_1.csv" through "channel_11.csv"
# csv_files <- paste0("channel_", 1:11, ".csv")

# 3. Connect to the DuckDB database (or create it if it doesn't exist)
con <- dbConnect(
  duckdb::duckdb(),
  "C:\\Users\\shish\\Documents\\rul_challenge_data\\DuckDB\\large_data_warehouse.duckdb"
)

# # ⭐️ DUCKDB PERFORMANCE TUNING (Add these lines here) ⭐️
# # Adjust '14GB' to a value slightly less than your total system RAM
# DBI::dbExecute(con, "SET memory_limit='14GB'")
# # Adjust '4' to a smaller number of cores than your system has
# DBI::dbExecute(con, "SET threads=1")
# # Note: You can also SET preserve_insertion_order=false if needed, but the two above are usually enough.
# # DBI::dbExecute(con, "SET preserve_insertion_order=false")

# start_time <- Sys.time()

# # 4. Loop through the folders to create schemas and load tables
# for (g_folder in g_folders) {
#   # A. Use the folder name as the schema name
#   schema_name <- g_folder

#   # B. Create the schema (this acts as your folder)
#   DBI::dbExecute(con, paste("CREATE SCHEMA IF NOT EXISTS", schema_name))
#   cat("Created schema:", schema_name, "\n")

#   # C. Loop through the CSVs within the current folder
#   for (csv_file in csv_files) {
#     # Construct the full file path for the CSV

#     base_path <- "C:\\Users\\shish\\Documents\\rul_challenge_data\\train"

#     full_path <- paste0(base_path, "/", g_folder, "/", csv_file)

#     # Check if the specific file exists before trying to load it
#     if (file.exists(full_path)) {
#       # The table name will be the CSV file name (e.g., 'channel_1')
#       table_name <- sub(".csv$", "", csv_file)

#       # Construct the full SQL table name: schema.table (e.g., G_1.channel_1)
#       full_table_name <- paste0(schema_name, ".", table_name)

#       # 1. Construct the SQL command
#       # CREATE OR REPLACE TABLE G_1.channel_1 AS SELECT * FROM READ_CSV_AUTO('full/path/to/file.csv')
#       sql_command <- paste0(
#         "CREATE TABLE IF NOT EXISTS ",
#         full_table_name,
#         " AS SELECT * FROM READ_CSV_AUTO('",
#         full_path,
#         "', HEADER=TRUE)"
#       )

#       # 2. Execute the SQL command
#       DBI::dbExecute(con, sql_command)

#       cat("  - Loaded table:", full_table_name, "\n")
#     }
#   }
# }

# end_time <- Sys.time()

# cat(
#   "Data loading completed in",
#   round(difftime(end_time, start_time, units = "mins"), 2),
#   "minutes.\n"
# )
```

I have loaded 2 tables into the database. Let me see if I can connect to the database and read some rows and columns.

```{r}

# G1

g1_channel1_lazy <- tbl(con, "G_1.channel_1")

g1_channel1_first_10_rows <- g1_channel1_lazy %>%
  head(10) %>%
  collect()

# Get first 10 rows and first 10 columns

g1_channel1_first_10_rows_first_10_cols <- g1_channel1_lazy %>%
  select(1:10) %>%
  head(10) %>%
  collect()

# Find number of rows and columns

g1_channel_1_num_rows <- g1_channel1_lazy %>%
  summarise(n = n()) %>%
  collect() %>%
  pull(n)

g1_channel_1_num_cols <- g1_channel1_lazy %>%
  colnames() %>%
  length()

g1_channel1_last_columns <- g1_channel1_lazy %>%
  select((num_cols - 9):num_cols) %>%
  head(10) %>%
  collect()

g1_channel2_lazy <- tbl(con, "G_1.channel_2")

g1_channel2_first_10_rows_2 <- g1_channel2_lazy %>%
  head(10) %>%
  collect()

# G2

g2_channel1_lazy <- tbl(con, "G_2.channel_1")

g2_channel1_num_rows <- g2_channel1_lazy %>%
  summarise(n = n()) %>%
  collect() %>%
  pull(n)

# G3

g3_channel1_lazy <- tbl(con, "G_3.channel_1")

g3_channel1_num_rows <- g3_channel1_lazy %>%
  summarise(n = n()) %>%
  collect() %>%
  pull(n)

# G4

g4_channel1_lazy <- tbl(con, "G_4.channel_1")

g4_channel1_num_rows <- g4_channel1_lazy %>%
  summarise(n = n()) %>%
  collect() %>%
  pull(n)

# G5

g5_channel1_lazy <- tbl(con, "G_5.channel_1")

g5_channel1_num_rows <- g5_channel1_lazy %>%
  summarise(n = n()) %>%
  collect() %>%
  pull(n)

# G6

g6_test_1_channel1_lazy <- tbl(con, "G_6_test_1.channel_1")

g6_test_1_channel1_first_10_rows_first_10_cols <- g6_test_1_channel1_lazy %>%
  select(1:10) %>%
  head(10) %>%
  collect()

g6_test_2_channel1_lazy <- tbl(con, "G_6_test_2.channel_1")
g6_test_2_channel1_first_10_rows_first_10_cols <- g6_test_2_channel1_lazy %>%
  select(1:10) %>%
  head(10) %>%
  collect()

g6_test_3_channel7_lazy <- tbl(con, "G_6_test_3.channel_7")
g6_test_3_channel7_first_10_rows_first_10_cols <- g6_test_3_channel7_lazy %>%
  select(1:10) %>%
  head(10) %>%
  collect()


dbDisconnect(con, shutdown = TRUE)

```

I could connect to the 2 tables using DuckDB. Note that I can only collect() 10 rows at a time since the number of columns is too large (32768). If I try 100 rows, R crashes.

Next, I also want to upload the test data to the DuckDB datbase.

```{r}
# # 1. Define the folder names (your "G" folders) and the test windows
# g_folders <- paste0("G_", 6)
# test_folders <- paste0("test_", 1:5)

# # 2. Define the CSV file names
# # Use a pattern that matches "channel_1.csv" through "channel_11.csv"
# csv_files <- paste0("channel_", 1:11, ".csv")

# # 3. Connect to the DuckDB database (or create it if it doesn't exist)
# con <- dbConnect(
#   duckdb::duckdb(),
#   "C:\\Users\\shish\\Documents\\rul_challenge_data\\DuckDB\\large_data_warehouse.duckdb"
# )

# # ⭐️ DUCKDB PERFORMANCE TUNING (Add these lines here) ⭐️
# # Adjust '14GB' to a value slightly less than your total system RAM
# DBI::dbExecute(con, "SET memory_limit='14GB'")
# # Adjust '4' to a smaller number of cores than your system has
# DBI::dbExecute(con, "SET threads=1")
# # Note: You can also SET preserve_insertion_order=false if needed, but the two above are usually enough.
# # DBI::dbExecute(con, "SET preserve_insertion_order=false")

# start_time <- Sys.time()

# # 4. Loop through the folders to create schemas and load tables
# for (g_folder in g_folders) {
#   for (test_folder in test_folders) {
#     # A. Use the folder name as the schema name
#     schema_name <- paste0(g_folder, "_", test_folder)

#     # B. Create the schema (this acts as your folder)
#     DBI::dbExecute(con, paste("CREATE SCHEMA IF NOT EXISTS", schema_name))
#     cat("Created schema:", schema_name, "\n")

#     # C. Loop through the CSVs within the current folder
#     for (csv_file in csv_files) {
#       # Construct the full file path for the CSV

#       base_path <- "C:\\Users\\shish\\Documents\\rul_challenge_data\\test"

#       full_path <- paste0(
#         base_path,
#         "/",
#         g_folder,
#         "/",
#         test_folder,
#         "/",
#         csv_file
#       )

#       # Check if the specific file exists before trying to load it
#       if (file.exists(full_path)) {
#         # The table name will be the CSV file name (e.g., 'channel_1')
#         table_name <- sub(".csv$", "", csv_file)

#         # Construct the full SQL table name: schema.table (e.g., G_6_test_1.channel_1)
#         full_table_name <- paste0(schema_name, ".", table_name)

#         # 1. Construct the SQL command
#         sql_command <- paste0(
#           "CREATE TABLE IF NOT EXISTS ",
#           full_table_name,
#           " AS SELECT * FROM READ_CSV_AUTO('",
#           full_path,
#           "', HEADER=TRUE)"
#         )

#         # 2. Execute the SQL command
#         DBI::dbExecute(con, sql_command)

#         cat("  - Loaded table:", full_table_name, "\n")
#       }
#     }
#   }
# }

# end_time <- Sys.time()

# cat(
#   "Test data loading completed in",
#   round(difftime(end_time, start_time, units = "mins"), 2),
#   "minutes.\n"
# )
```

Test folders loaded. Check if I can connect to one of the test tables.

```{r}
g6_test1_channel1_lazy <- tbl(con, "G_6_test_1.channel_1")

first_10_rows_test <- g6_test1_channel1_lazy %>%
  head(10) %>%
  collect()

g6_test5_channel11_lazy <- tbl(con, "G_6_test_5.channel_11")

first_10_rows_test <- g6_test5_channel11_lazy %>%
  head(10) %>%
  collect()
```


See if there is a faster way to load each rows since there are too many columns.

```{r}
g1_channel1_lazy <- tbl(con, "G_1.channel_1")

start_time <- Sys.time()
g1_channel1_first_1_rows <- g1_channel1_lazy %>%
  head(1) %>%
  collect() %>%
  unlist() %>%
  as.numeric()

w_len <- 256
spec_gram <- specgram(
  x = g1_channel1_first_1_rows,
  n = 1024,
  Fs = 12800,
  overlap = 0.8 * w_len,
  window = hanning(w_len)
)

end_time <- Sys.time()
cat(
  "Time taken to load 1 row with",
  length(g1_channel1_first_1_rows),
  "columns:",
  round(difftime(end_time, start_time, units = "secs"), 2),
  "seconds.\n"
)

g1_channel1_lazy_df <- g1_channel1_lazy %>%
  collect()
```

But the evaluation is too slow. It took 14 minutes to load 2 tables. I need to load almost 60 tables.

Try data.table

```{r}
# install.packages("data.table") # Run this once if you don't have the package
library(data.table)

# Use forward slashes for clarity
file_path <- "C:/Users/shish/Documents/rul_challenge_data/train/G_1/channel_1.csv"

# Load the data frame quickly
data_fast <- fread(file_path)
```

Convert CSV to Parquet format for faster loading.

```{r}
con <- dbConnect(duckdb::duckdb())
dbExecute(
  con,
  "COPY 'G:\\My Drive\\rao@ualberta.ca 2022-12-08 10 58\\shishir@tamu.edu\\My Drive\\Interesting papers\\Survival Models\\Reliability\\RUL Challenge\\rul_challenge_data\\rul_challenge_data\\train\\G_1\\channel_1.csv' TO 'G:\\My Drive\\rao@ualberta.ca 2022-12-08 10 58\\shishir@tamu.edu\\My Drive\\Interesting papers\\Survival Models\\Reliability\\RUL Challenge\\rul_challenge_data\\parquet\\G_1_channel_1.parquet' (FORMAT PARQUET);"
)
dbDisconnect(con)
```

Next, I will try sparklyr to load the data.

```{r}
# Run this once to install a local version of Spark that sparklyr can use
# sparklyr::spark_install()
```

Connecting and loading data with sparklyr.

```{r}
# 1. Connect to a local Spark instance (using all available cores)
# The 'sc' object is your Spark connection handle.
sc <- sparklyr::spark_connect(master = "local[*]")

# 2. Define your file structure parameters
g_folders <- paste0("G_", 1:1) # Assuming you go back to all 5 folders
csv_files <- paste0("channel_", 1:1, ".csv")

# 3. Define the base path for your data
base_path <- "G:/My Drive/rao@ualberta.ca 2022-12-08 10 58/shishir@tamu.edu/My Drive/Interesting papers/Survival Models/Reliability/RUL Challenge/rul_challenge_data/rul_challenge_data/train"

# 4. Loop through the folders to load and register tables
for (g_folder in g_folders) {
  # The table name in Spark will be: schema_table (e.g., G_1_channel_1)
  schema_prefix <- paste0(g_folder, "_")

  # C. Loop through the CSVs within the current folder
  for (csv_file in csv_files) {
    # Construct the full file path for the CSV
    full_path <- file.path(base_path, g_folder, csv_file)

    # The full path Spark needs uses the 'file:///' prefix for local access
    spark_file_path <- paste0("file:///", full_path)

    # Check if the specific file exists before trying to load it
    # Note: Spark's reader is very robust, but checking in R first is good practice
    if (file.exists(full_path)) {
      table_suffix <- sub(".csv$", "", csv_file)
      full_table_name <- paste0(schema_prefix, table_suffix)

      cat("Loading and registering table:", full_table_name, "\n")

      # ⭐️ THE KEY STEP: Use spark_read_csv for efficient loading ⭐️
      # This reads the CSV in a distributed, parallel fashion,
      # registers it as a lazy table in Spark, and handles the header.
      sparklyr::spark_read_csv(
        sc = sc,
        name = full_table_name,
        path = spark_file_path,
        header = TRUE,
        infer_schema = TRUE, # Infers column data types from the data
        overwrite = TRUE, # Overwrite if table exists (can change to FALSE if preferred)
        options = list(maxColumns = 40000L) # Set a value greater than 32768
      )
      cat(" - Registered table:", full_table_name, "\n")
    }
  }
}
```


```{r}
# 1. Define the folder names (your "G" folders)
g_folders <- paste0("G_", 1:1)

# 2. Define the CSV file names
# Use a pattern that matches "channel_1.csv" through "channel_11.csv"
csv_files <- paste0("channel_", 1:1, ".csv")

# 3. Connect to the DuckDB database (or create it if it doesn't exist)
con <- dbConnect(duckdb::duckdb(), "large_data_warehouse.duckdb")

# 4. Loop through the folders to create schemas and load tables
for (g_folder in g_folders) {
  # A. Use the folder name as the schema name
  schema_name <- g_folder

  # B. Create the schema (this acts as your folder)
  DBI::dbExecute(con, paste("CREATE SCHEMA IF NOT EXISTS", schema_name))
  cat("Created schema:", schema_name, "\n")

  # C. Loop through the CSVs within the current folder
  for (csv_file in csv_files) {
    # Construct the full file path for the CSV

    base_path <- "G:/My Drive/rao@ualberta.ca 2022-12-08 10 58/shishir@tamu.edu/My Drive/Interesting papers/Survival Models/Reliability/RUL Challenge/rul_challenge_data/rul_challenge_data/train"

    full_path <- paste0(base_path, "/", g_folder, "/", csv_file)

    # Check if the specific file exists before trying to load it
    if (file.exists(full_path)) {
      # The table name will be the CSV file name (e.g., 'channel_1')
      table_name <- sub(".csv$", "", csv_file)

      # Construct the full SQL table name: schema.table (e.g., G_1.channel_1)
      full_table_name <- paste0(schema_name, ".", table_name)

      # Option A: let DuckDB read the CSV directly (fast, avoids R memory)
      full_path_escaped <- gsub("'", "''", full_path) # escape single quotes if any
      sql <- paste0(
        "CREATE TABLE ",
        full_table_name,
        " AS SELECT * FROM read_csv_auto('",
        full_path_escaped,
        "')"
      )
      DBI::dbExecute(con, sql)

      # # Load the large CSV directly into the DuckDB table
      # # Use dbplyr/DBI to run the appropriate SQL for bulk loading
      # dbWriteTable(
      #   conn = con,
      #   name = full_table_name,
      #   value = full_path, # DuckDB efficiently reads the file from this path
      #   header = TRUE,
      #   row.names = FALSE,
      #   overwrite = TRUE
      # )
      cat("  - Loaded table:", full_table_name, "\n")
    }
  }
}
```

```{r}
G_1_channel_1 <- read.csv(
  "G:\\My Drive\\rao@ualberta.ca 2022-12-08 10 58\\shishir@tamu.edu\\My Drive\\Interesting papers\\Survival Models\\Reliability\\RUL Challenge\\rul_challenge_data\\rul_challenge_data\\train\\G_1\\channel_1.csv"
)
```

ROUGH


```{r}
# 1. Find the path to your default user library
default_library_path <- .libPaths()[[1]]

# 2. Install the package explicitly to that path
install.packages("DBI", lib = default_library_path)
```