---
title: "Untitled"
format: html
---


This document is used to plot power(dB) vs frequency, Power (RMS) vs frequency and spectral kurtosis vs frequency   graph for 5 different window sizes (32, 64, 128, 256, 512). I want 80% overlap. For a given channel, I will plot every 30th signal. This will give me an idea about the dominant frequencies present in the signal for different window sizes. Once you have this plot, take a decision on the window size to be used for further analysis. Please give me the code. Like before, I want to visualize the different window sizes in the same plot for comparison. Also, like before, I want a plotly plot where each frame is a signal. I want a function that takes in a channel and outputs a plotly plot. Please give me the code. 

```{r}

# renv::install("signal")
# renv::install("e1071")
# renv::install("av")
# renv::install("future")
# renv::install("furrr")
# renv::install("plotly")
# renv::install("htmlwidgets")
# renv::install("pracma")

library(tidyverse)
library(DBI)
library(duckdb)
library(sparklyr)
library(signal)
library(e1071)
library(av)
library(parallel)
library(future)
library(furrr)
library(data.table)
library(plotly)
library(htmlwidgets)
library(pracma)
```


FULL Code ::

```{r}
# ============================================================================
# PREPROCESSING FUNCTIONS
# ============================================================================

preprocess_signal <- function(signal_vector, Fs = 12800) {
  # Step 1: Detrending - Remove the mean
  detrended_signal <- signal_vector - mean(signal_vector)

  # Step 2: Low-pass filtering
  nyquist_freq <- Fs / 2
  cutoff_freq <- 1 * nyquist_freq
  W <- cutoff_freq / nyquist_freq

  # Design Butterworth filter (4th order)
  butter_filter <- butter(n = 4, W = W, type = "low")

  # Apply the filter
  filtered_signal <- filtfilt(butter_filter, detrended_signal)

  return(filtered_signal)
}

calculate_vibration_timeDomainFeatures <- function(signal_vector) {
  abs_signal <- abs(signal_vector)
  peak_value <- max(abs_signal)
  rms_value <- sqrt(mean(signal_vector^2))
  abs_mean <- mean(abs_signal)
  margin_denominator <- (abs_mean)^2

  results <- list(
    Mean = mean(signal_vector),
    Std_Dev = sd(signal_vector),
    Peak_to_Peak = max(signal_vector) - min(signal_vector),
    RMS = rms_value,
    Skewness = skewness(signal_vector),
    Kurtosis = kurtosis(signal_vector),
    Crest_Factor = peak_value / rms_value,
    Shape_Factor = rms_value / abs_mean,
    Impulse_Factor = peak_value / abs_mean,
    Margin_Factor = peak_value / margin_denominator,
    Energy = sum(signal_vector^2)
  )

  return(results)
}

# ============================================================================
# STAGE 1: FAST SPECTRAL FINGERPRINTING (GMF-BASED) - MEMORY OPTIMIZED
# ============================================================================

extract_spectral_fingerprint <- function(
  signal,
  Fs = 12800,
  preprocess = TRUE,
  freq_min = 10,
  freq_max = 6400,
  gearbox_group = "G_1_to_G_3"
) {
  if (preprocess) {
    signal <- preprocess_signal(signal)
  }

  # Compute FFT
  n <- length(signal)
  fft_result <- fft(signal)
  magnitude <- Mod(fft_result[1:(n / 2)])
  freqs <- (0:(n / 2 - 1)) * Fs / n

  # Use full frequency range (exclude only DC and very low freq)
  freq_mask <- freqs >= freq_min & freqs <= freq_max
  magnitude_filtered <- magnitude[freq_mask]
  freqs_filtered <- freqs[freq_mask]

  # Define gear mesh frequencies
  GMF1 <- 1160 # Test gearbox: Input-Intermediate mesh
  GMF2 <- 439.6 # Test gearbox: Intermediate-Output mesh (PINION - FAILURE LOCATION)

  # Extract energy at GMF harmonics
  extract_gmf_harmonics <- function(gmf, n_harmonics = 5, bandwidth = 50) {
    harmonic_energies <- numeric(n_harmonics)
    for (h in 1:n_harmonics) {
      freq_center <- gmf * h
      freq_range <- (freqs_filtered >= (freq_center - bandwidth)) &
        (freqs_filtered <= (freq_center + bandwidth))
      if (sum(freq_range) > 0) {
        harmonic_energies[h] <- sum(magnitude_filtered[freq_range]^2)
      } else {
        harmonic_energies[h] <- 0
      }
    }
    return(harmonic_energies)
  }

  # Extract GMF harmonics
  gmf1_harmonics <- extract_gmf_harmonics(GMF1, n_harmonics = 3)
  gmf2_harmonics <- extract_gmf_harmonics(GMF2, n_harmonics = 5)

  # Standard spectral features
  total_energy <- sum(magnitude_filtered^2)

  spectral_centroid <- sum(freqs_filtered * magnitude_filtered) /
    sum(magnitude_filtered)

  spectral_spread <- sqrt(
    sum(((freqs_filtered - spectral_centroid)^2) * magnitude_filtered) /
      sum(magnitude_filtered)
  )

  cumsum_energy <- cumsum(magnitude_filtered^2)
  rolloff_idx <- which(cumsum_energy >= 0.85 * total_energy)[1]
  spectral_rolloff <- freqs_filtered[rolloff_idx]

  rms <- sqrt(mean(signal^2))

  # High frequency energy ratio
  high_freq_mask <- freqs_filtered >= 3000
  high_freq_energy_ratio <- sum(magnitude_filtered[high_freq_mask]^2) /
    total_energy

  return(c(
    Spectral_Centroid = spectral_centroid,
    Spectral_Spread = spectral_spread,
    Spectral_Rolloff = spectral_rolloff,
    RMS = rms,
    High_Freq_Energy_Ratio = high_freq_energy_ratio,
    GMF2_H1 = gmf2_harmonics[1],
    GMF2_H2 = gmf2_harmonics[2],
    GMF2_H3 = gmf2_harmonics[3],
    GMF2_H4 = gmf2_harmonics[4],
    GMF2_H5 = gmf2_harmonics[5],
    GMF1_H1 = gmf1_harmonics[1],
    GMF1_H2 = gmf1_harmonics[2],
    GMF1_H3 = gmf1_harmonics[3]
  ))
}

precompute_spectral_fingerprints <- function(
  gearbox_path,
  channels = c(4, 5, 9),
  gearbox_name = "Gearbox",
  gearbox_group = NULL
) {
  cat("=== Computing spectral fingerprints for", gearbox_name, "===\n")

  # Auto-detect gearbox group
  if (is.null(gearbox_group)) {
    if (grepl("G_[123]", gearbox_path)) {
      gearbox_group <- "G_1_to_G_3"
    } else if (grepl("G_[456]", gearbox_path)) {
      gearbox_group <- "G_4_to_G_6"
    } else {
      warning("Could not detect gearbox group, defaulting to G_1_to_G_3")
      gearbox_group <- "G_1_to_G_3"
    }
  }

  cat("Detected gearbox group:", gearbox_group, "\n")

  # Get number of signals by reading only the first channel's row count
  channel_1_path <- file.path(
    gearbox_path,
    paste0("channel_", channels[1], ".csv")
  )
  n_signals <- nrow(fread(channel_1_path, select = 1L, header = TRUE)) # Only read first column to count rows

  cat("Total signals:", n_signals, "\n")

  # Initialize matrix
  fingerprints_matrix <- matrix(nrow = n_signals, ncol = 13)
  colnames(fingerprints_matrix) <- c(
    "Spectral_Centroid",
    "Spectral_Spread",
    "Spectral_Rolloff",
    "RMS",
    "High_Freq_Energy_Ratio",
    "GMF2_H1",
    "GMF2_H2",
    "GMF2_H3",
    "GMF2_H4",
    "GMF2_H5",
    "GMF1_H1",
    "GMF1_H2",
    "GMF1_H3"
  )

  # Process each signal
  for (signal_idx in 1:n_signals) {
    # Average fingerprint across selected channels
    channel_fingerprints <- matrix(nrow = length(channels), ncol = 13)

    for (i in seq_along(channels)) {
      ch <- channels[i]
      channel_path <- file.path(gearbox_path, paste0("channel_", ch, ".csv"))

      # Read ONLY this one signal (one row) - MEMORY OPTIMIZED!
      signal <- fread(
        channel_path,
        skip = signal_idx - 1, # Skip to the specific row
        nrows = 1, # Read only 1 row
        header = TRUE
      ) |>
        unlist() |>
        as.numeric()

      channel_fingerprints[i, ] <- extract_spectral_fingerprint(
        signal,
        gearbox_group = gearbox_group
      )
    }

    # Average across channels
    fingerprints_matrix[signal_idx, ] <- colMeans(
      channel_fingerprints,
      na.rm = TRUE
    )

    # Progress every 10 signals
    if (signal_idx %% 10 == 0) {
      cat("  Processed", signal_idx, "of", n_signals, "\n")
    }
  }

  rownames(fingerprints_matrix) <- paste0("Signal_", 1:n_signals)
  cat("Fingerprint extraction complete!\n\n")

  return(fingerprints_matrix)
}

compute_fingerprint_similarity <- function(
  test_fingerprints,
  train_fingerprints
) {
  # Normalize both
  test_norm <- scale(test_fingerprints)
  train_norm <- scale(train_fingerprints)

  # Flatten and compute cosine similarity
  test_vec <- as.vector(t(test_norm))
  train_vec <- as.vector(t(train_norm))

  # Remove NAs
  valid_idx <- !is.na(test_vec) & !is.na(train_vec)

  cosine_sim <- sum(test_vec[valid_idx] * train_vec[valid_idx]) /
    (sqrt(sum(test_vec[valid_idx]^2)) * sqrt(sum(train_vec[valid_idx]^2)))

  return(cosine_sim)
}

fast_candidate_selection_optimized <- function(
  test_gearbox_path,
  train_gearbox_path,
  test_signal_indices = 1:5,
  top_n_candidates = 50,
  fingerprint_channels = c(4, 5, 9),
  full_feature_channels = 1:11,
  test_gearbox = NULL, # Add this
  test_set = NULL, # Add this
  train_gearbox = NULL # Add this
) {
  cat("=== Stage 1: Fast Spectral Fingerprint Screening ===\n")
  cat(
    "Using channels:",
    paste(fingerprint_channels, collapse = ", "),
    "(Output shaft vibrations + Acoustic emission)\n"
  )
  cat("Focusing on pinion failure signatures (GMF harmonics)\n\n")

  # Create cache file names
  test_cache_file <- paste0(
    "fingerprints_",
    test_gearbox,
    "_",
    test_set,
    "_ch",
    paste(fingerprint_channels, collapse = "_"),
    ".rds"
  )

  train_cache_file <- paste0(
    "fingerprints_",
    train_gearbox,
    "_ch",
    paste(fingerprint_channels, collapse = "_"),
    ".rds"
  )

  # Check if test fingerprints exist, otherwise compute
  if (file.exists(test_cache_file)) {
    cat("Loading cached test fingerprints from:", test_cache_file, "\n")
    test_fingerprints_all <- readRDS(test_cache_file)
  } else {
    cat("Computing test fingerprints...\n")
    test_fingerprints_all <- precompute_spectral_fingerprints(
      test_gearbox_path,
      channels = fingerprint_channels,
      gearbox_name = basename(test_gearbox_path)
    )
    saveRDS(test_fingerprints_all, test_cache_file)
    cat("Saved test fingerprints to:", test_cache_file, "\n")
  }

  # Check if train fingerprints exist, otherwise compute
  if (file.exists(train_cache_file)) {
    cat("Loading cached train fingerprints from:", train_cache_file, "\n")
    train_fingerprints_all <- readRDS(train_cache_file)
  } else {
    cat("Computing train fingerprints...\n")
    train_fingerprints_all <- precompute_spectral_fingerprints(
      train_gearbox_path,
      channels = fingerprint_channels,
      gearbox_name = basename(train_gearbox_path)
    )
    saveRDS(train_fingerprints_all, train_cache_file)
    cat("Saved train fingerprints to:", train_cache_file, "\n")
  }

  # Extract test trajectory
  test_trajectory <- test_fingerprints_all[test_signal_indices, ]

  n_train <- nrow(train_fingerprints_all)
  window_size <- length(test_signal_indices)
  n_windows <- n_train - window_size + 1

  cat("Screening", n_windows, "windows...\n")

  similarities <- numeric(n_windows)

  for (i in 1:n_windows) {
    train_window <- train_fingerprints_all[i:(i + window_size - 1), ]
    similarities[i] <- compute_fingerprint_similarity(
      test_trajectory,
      train_window
    )

    if (i %% 200 == 0) {
      cat("  Screened", i, "of", n_windows, "windows\n")
    }
  }

  # Get top N candidates
  top_indices <- order(similarities, decreasing = TRUE)[1:top_n_candidates]

  candidates <- data.frame(
    Window_Start = top_indices,
    Window_End = top_indices + window_size - 1,
    Fingerprint_Similarity = similarities[top_indices]
  )

  cat("\nTop", top_n_candidates, "candidates selected\n")
  cat(
    "Similarity range:",
    round(min(candidates$Fingerprint_Similarity), 3),
    "to",
    round(max(candidates$Fingerprint_Similarity), 3),
    "\n\n"
  )

  return(list(
    candidates = candidates,
    test_fingerprints = test_fingerprints_all,
    train_fingerprints = train_fingerprints_all,
    full_feature_channels = full_feature_channels
  ))
}

# ============================================================================
# STAGE 2: FULL FEATURE EXTRACTION - MEMORY OPTIMIZED
# ============================================================================

precompute_all_features <- function(
  gearbox_path,
  channels = 1:11,
  preprocess = TRUE,
  gearbox_name = "Gearbox"
) {
  cat("=== Pre-computing features for", gearbox_name, "===\n")

  # Get number of signals by reading only first column
  channel_1_path <- file.path(gearbox_path, "channel_1.csv")
  n_signals <- nrow(fread(channel_1_path, select = 1L, header = TRUE)) # Only read first column to count rows

  cat("Total signals:", n_signals, "\n")
  cat("Channels:", length(channels), "\n")

  all_features_matrix <- NULL
  feature_names <- NULL

  for (signal_idx in 1:n_signals) {
    signal_features <- list()

    for (ch in channels) {
      channel_path <- file.path(gearbox_path, paste0("channel_", ch, ".csv"))

      # Read ONLY this one signal (one row) - MEMORY OPTIMIZED!
      signal <- fread(
        channel_path,
        skip = signal_idx - 1,
        nrows = 1,
        header = TRUE
      ) |>
        unlist() |>
        as.numeric()

      if (preprocess) {
        signal <- preprocess_signal(signal)
      }

      # Time-domain features
      td_features <- calculate_vibration_timeDomainFeatures(signal)

      # Frequency-domain features (spectral kurtosis summary)
      w_len <- 128
      o_len <- 0.8 * w_len

      spec_output <- specgram(
        signal,
        n = 512,
        Fs = 12800,
        overlap = o_len,
        window = hanning(w_len)
      )

      P_matrix <- Mod(spec_output$S)^2
      freq_bins <- spec_output$f

      # Exclude DC bin
      P_data <- P_matrix[-1, ]
      freq_data <- freq_bins[-1]

      # Calculate SK for frequency range >= 10 Hz (full range)
      freq_mask <- freq_data >= 10

      if (sum(freq_mask) > 0) {
        P_data_filtered <- P_data[freq_mask, ]

        num_freq_bins <- nrow(P_data_filtered)
        sk_values <- numeric(num_freq_bins)

        for (i in 1:num_freq_bins) {
          energy_envelope <- P_data_filtered[i, ]
          sk_values[i] <- e1071::kurtosis(energy_envelope, type = 1) + 1
        }

        sk_mean <- mean(sk_values, na.rm = TRUE)
        sk_max <- max(sk_values, na.rm = TRUE)
        sk_std <- sd(sk_values, na.rm = TRUE)
      } else {
        sk_mean <- NA
        sk_max <- NA
        sk_std <- NA
      }

      # Combine all features for this channel
      channel_features <- c(
        unlist(td_features),
        SK_Mean = sk_mean,
        SK_Max = sk_max,
        SK_Std = sk_std
      )

      # Add channel prefix to feature names
      names(channel_features) <- paste0("Ch", ch, ".", names(channel_features))
      signal_features[[ch]] <- channel_features
    }

    # Flatten features for this signal
    signal_feature_vector <- unlist(signal_features)

    # Initialize matrix on first signal
    if (is.null(all_features_matrix)) {
      n_features <- length(signal_feature_vector)
      all_features_matrix <- matrix(nrow = n_signals, ncol = n_features)
      feature_names <- names(signal_feature_vector)
      colnames(all_features_matrix) <- feature_names
    }

    all_features_matrix[signal_idx, ] <- signal_feature_vector

    # Progress every 10 signals
    if (signal_idx %% 10 == 0) {
      cat("  Processed signal", signal_idx, "of", n_signals, "\n")
    }
  }

  rownames(all_features_matrix) <- paste0("Signal_", 1:n_signals)

  cat("Feature extraction complete!\n")
  cat(
    "Matrix dimensions:",
    nrow(all_features_matrix),
    "signals x",
    ncol(all_features_matrix),
    "features\n\n"
  )

  return(all_features_matrix)
}

extract_trajectory_from_precomputed <- function(
  features_matrix,
  signal_indices
) {
  return(features_matrix[signal_indices, , drop = FALSE])
}

compare_trajectories <- function(trajectory1, trajectory2) {
  # Ensure same number of time points
  if (nrow(trajectory1) != nrow(trajectory2)) {
    stop("Trajectories must have the same number of time points")
  }

  if (ncol(trajectory1) != ncol(trajectory2)) {
    stop("Trajectories must have the same features")
  }

  n_timepoints <- nrow(trajectory1)
  n_features <- ncol(trajectory1)

  # Method 1: Correlation of feature trends
  correlations <- numeric(n_features)
  for (i in 1:n_features) {
    correlations[i] <- cor(
      trajectory1[, i],
      trajectory2[, i],
      use = "complete.obs"
    )
  }
  mean_correlation <- mean(correlations, na.rm = TRUE)

  # Method 2: Euclidean distance between normalized trajectories
  traj1_norm <- scale(trajectory1)
  traj2_norm <- scale(trajectory2)
  euclidean_dist <- sqrt(sum((traj1_norm - traj2_norm)^2, na.rm = TRUE))

  # Method 3: Cosine similarity of flattened trajectories
  vec1 <- as.vector(t(traj1_norm))
  vec2 <- as.vector(t(traj2_norm))
  valid_idx <- !is.na(vec1) & !is.na(vec2)
  cosine_sim <- sum(vec1[valid_idx] * vec2[valid_idx]) /
    (sqrt(sum(vec1[valid_idx]^2)) * sqrt(sum(vec2[valid_idx]^2)))

  return(list(
    mean_correlation = mean_correlation,
    euclidean_distance = euclidean_dist,
    cosine_similarity = cosine_sim
  ))
}

refine_candidates_with_full_features <- function(
  test_gearbox_path,
  train_gearbox_path,
  candidates,
  test_signal_indices = 1:5,
  test_features = NULL,
  train_features = NULL,
  channels = 1:11,
  preprocess = TRUE
) {
  cat("=== Stage 2: Full Feature Comparison on Top Candidates ===\n")

  # Pre-compute test features if not provided (only 5 signals)
  if (is.null(test_features)) {
    test_features <- precompute_all_features(
      test_gearbox_path,
      channels,
      preprocess,
      "Test"
    )
  }

  # For train features: extract only for candidate windows
  # Identify unique signal indices needed
  unique_train_signals <- unique(unlist(lapply(1:nrow(candidates), function(i) {
    candidates$Window_Start[i]:candidates$Window_End[i]
  })))
  unique_train_signals <- sort(unique_train_signals)

  cat(
    "Need features for",
    length(unique_train_signals),
    "unique train signals (from 50 windows)\n"
  )

  if (is.null(train_features)) {
    # Compute features ONLY for needed signals
    train_features_map <- list()

    for (sig_idx in unique_train_signals) {
      signal_features <- list()

      for (ch in channels) {
        channel_path <- file.path(
          train_gearbox_path,
          paste0("channel_", ch, ".csv")
        )

        signal <- fread(
          channel_path,
          skip = sig_idx - 1,
          nrows = 1,
          header = TRUE
        ) |>
          unlist() |>
          as.numeric()

        if (preprocess) {
          signal <- preprocess_signal(signal)
        }

        # Time-domain features
        td_features <- calculate_vibration_timeDomainFeatures(signal)

        # Frequency-domain features
        w_len <- 128
        o_len <- 0.8 * w_len

        spec_output <- specgram(
          signal,
          n = 512,
          Fs = 12800,
          overlap = o_len,
          window = hanning(w_len)
        )

        P_matrix <- Mod(spec_output$S)^2
        freq_bins <- spec_output$f
        P_data <- P_matrix[-1, ]
        freq_data <- freq_bins[-1]

        freq_mask <- freq_data >= 10

        if (sum(freq_mask) > 0) {
          P_data_filtered <- P_data[freq_mask, ]
          num_freq_bins <- nrow(P_data_filtered)
          sk_values <- numeric(num_freq_bins)

          for (i in 1:num_freq_bins) {
            energy_envelope <- P_data_filtered[i, ]
            sk_values[i] <- e1071::kurtosis(energy_envelope, type = 1) + 1
          }

          sk_mean <- mean(sk_values, na.rm = TRUE)
          sk_max <- max(sk_values, na.rm = TRUE)
          sk_std <- sd(sk_values, na.rm = TRUE)
        } else {
          sk_mean <- NA
          sk_max <- NA
          sk_std <- NA
        }

        channel_features <- c(
          unlist(td_features),
          SK_Mean = sk_mean,
          SK_Max = sk_max,
          SK_Std = sk_std
        )

        names(channel_features) <- paste0(
          "Ch",
          ch,
          ".",
          names(channel_features)
        )
        signal_features[[ch]] <- channel_features
      }

      train_features_map[[as.character(sig_idx)]] <- unlist(signal_features)

      if (which(unique_train_signals == sig_idx) %% 10 == 0) {
        cat(
          "  Extracted features for",
          which(unique_train_signals == sig_idx),
          "of",
          length(unique_train_signals),
          "signals\n"
        )
      }
    }
  }

  # Extract test trajectory
  test_trajectory <- extract_trajectory_from_precomputed(
    test_features,
    test_signal_indices
  )

  # Compare with candidates
  refined_results <- data.frame(
    Window_Start = integer(),
    Window_End = integer(),
    Fingerprint_Similarity = numeric(),
    Mean_Correlation = numeric(),
    Euclidean_Distance = numeric(),
    Cosine_Similarity = numeric()
  )

  for (i in 1:nrow(candidates)) {
    start_idx <- candidates$Window_Start[i]
    end_idx <- candidates$Window_End[i]
    window_indices <- start_idx:end_idx

    # Build train window from extracted features
    train_window <- matrix(
      nrow = length(window_indices),
      ncol = length(train_features_map[[1]])
    )
    for (j in seq_along(window_indices)) {
      train_window[j, ] <- train_features_map[[as.character(window_indices[j])]]
    }
    colnames(train_window) <- names(train_features_map[[1]])

    similarity <- compare_trajectories(test_trajectory, train_window)

    refined_results <- rbind(
      refined_results,
      data.frame(
        Window_Start = start_idx,
        Window_End = end_idx,
        Fingerprint_Similarity = candidates$Fingerprint_Similarity[i],
        Mean_Correlation = similarity$mean_correlation,
        Euclidean_Distance = similarity$euclidean_distance,
        Cosine_Similarity = similarity$cosine_similarity
      )
    )

    if (i %% 10 == 0) {
      cat("  Refined", i, "of", nrow(candidates), "candidates\n")
    }
  }

  # Compute composite score
  refined_results$Euclidean_Distance_Norm <- 1 -
    (refined_results$Euclidean_Distance -
      min(refined_results$Euclidean_Distance)) /
      (max(refined_results$Euclidean_Distance) -
        min(refined_results$Euclidean_Distance))

  refined_results$Composite_Score <- (refined_results$Mean_Correlation +
    refined_results$Cosine_Similarity +
    refined_results$Euclidean_Distance_Norm) /
    3

  refined_results <- refined_results |> arrange(desc(Composite_Score))

  cat("\n=== Refinement Complete ===\n")

  return(refined_results)
}

# ============================================================================
# COMPLETE PIPELINE
# ============================================================================

find_degradation_stage_fast_optimized <- function(
  test_gearbox = "G_6",
  test_set = "test_1",
  test_signal_indices = 1:5,
  train_gearbox = "G_1",
  base_path = "C:/Users/shish/Documents/rul_challenge_data",
  fingerprint_channels = c(4, 5, 9), # Output shaft + acoustic for Stage 1
  full_feature_channels = 1:11, # All channels for Stage 2
  top_n_candidates = 50,
  preprocess = TRUE,
  test_features = NULL,
  train_features = NULL
) {
  test_path <- file.path(base_path, "test", test_gearbox, test_set)
  train_path <- file.path(base_path, "train", train_gearbox)

  # Stage 1: Fast screening with GMF-based fingerprints
  stage1_output <- fast_candidate_selection_optimized(
    test_path,
    train_path,
    test_signal_indices,
    top_n_candidates,
    fingerprint_channels,
    full_feature_channels,
    test_gearbox = test_gearbox, # Pass the value
    test_set = test_set, # Pass the value
    train_gearbox = train_gearbox # Pass the value
  )

  # Stage 2: Refined comparison with all channels
  final_results <- refine_candidates_with_full_features(
    test_path,
    train_path,
    stage1_output$candidates,
    test_signal_indices,
    test_features = test_features,
    train_features = train_features,
    channels = full_feature_channels,
    preprocess = preprocess
  )

  return(list(
    results = final_results,
    stage1_output = stage1_output
  ))
}

plot_degradation_matching <- function(results, train_gearbox = "G_1") {
  # Find best matches
  best_correlation <- results[which.max(results$Mean_Correlation), ]
  best_cosine <- results[which.max(results$Cosine_Similarity), ]
  best_euclidean <- results[which.min(results$Euclidean_Distance), ]
  best_composite <- results[which.max(results$Composite_Score), ]

  # Create interactive plot
  fig <- plot_ly(results, x = ~Window_Start) |>
    add_trace(
      y = ~Mean_Correlation,
      name = "Mean Correlation",
      type = 'scatter',
      mode = 'lines+markers',
      line = list(width = 2)
    ) |>
    add_trace(
      y = ~Cosine_Similarity,
      name = "Cosine Similarity",
      type = 'scatter',
      mode = 'lines+markers',
      line = list(width = 2)
    ) |>
    add_trace(
      y = ~Euclidean_Distance_Norm,
      name = "Euclidean (Normalized)",
      type = 'scatter',
      mode = 'lines+markers',
      line = list(width = 2)
    ) |>
    add_trace(
      y = ~Composite_Score,
      name = "Composite Score",
      type = 'scatter',
      mode = 'lines+markers',
      line = list(width = 2, dash = 'dash')
    ) |>
    layout(
      title = paste("G_6 Degradation Stage Matching with", train_gearbox),
      xaxis = list(title = paste(train_gearbox, "Signal Window Start Index")),
      yaxis = list(title = "Similarity Score", range = c(0, 1)),
      hovermode = "x unified"
    )

  # Print summary
  cat("\n=== Best Matches ===\n")
  cat(
    "By Mean Correlation:",
    best_correlation$Window_Start,
    "-",
    best_correlation$Window_End,
    "(score:",
    round(best_correlation$Mean_Correlation, 3),
    ")\n"
  )
  cat(
    "By Cosine Similarity:",
    best_cosine$Window_Start,
    "-",
    best_cosine$Window_End,
    "(score:",
    round(best_cosine$Cosine_Similarity, 3),
    ")\n"
  )
  cat(
    "By Euclidean Distance:",
    best_euclidean$Window_Start,
    "-",
    best_euclidean$Window_End,
    "(score:",
    round(best_euclidean$Euclidean_Distance, 2),
    ")\n"
  )
  cat(
    "By Composite Score:",
    best_composite$Window_Start,
    "-",
    best_composite$Window_End,
    "(score:",
    round(best_composite$Composite_Score, 3),
    ")\n"
  )

  return(fig)
}
```


Using Cepstrum code from Gemini

```{r}
library(data.table)
library(dplyr)
library(signal)
library(e1071)
library(pracma)
library(plotly)

# ============================================================================
# HELPER 1: SHAFT SPEED FROM KEY PHASOR (Channel 7)
# ============================================================================
get_shaft_speed_from_keyphasor <- function(keyphasor_vec, Fs = 12800) {
  # 1. Normalize and Threshold
  # Key phasor is a pulse train. We find the rising edges.
  thresh <- (max(keyphasor_vec) - min(keyphasor_vec)) * 0.5 + min(keyphasor_vec)

  # 2. Find rising edges (0 -> 1 transitions)
  pulse_binary <- as.integer(keyphasor_vec > thresh)
  rising_edges <- which(diff(pulse_binary) == 1)

  if (length(rising_edges) < 2) {
    return(list(hz = NA, edges = c()))
  }

  # 3. Calculate average speed
  avg_samples_diff <- mean(diff(rising_edges))
  shaft_freq_hz <- Fs / avg_samples_diff

  return(list(hz = shaft_freq_hz, edges = rising_edges))
}

# ============================================================================
# HELPER 2: CEPSTRUM RAHMONIC AMPLITUDE (Stage 1 Feature)
# ============================================================================
compute_cepstrum_features <- function(signal_vec, Fs, input_shaft_hz) {
  n <- length(signal_vec)

  # 1. Gear Kinematics
  # Input: 2400 RPM (40 Hz). Pinion is on Intermediate Shaft.
  # Ratio: Input(29T) -> Intermediate(95T)
  intermediate_shaft_hz <- input_shaft_hz * (29 / 95)

  # 2. Real Cepstrum
  spec <- Mod(fft(signal_vec))
  log_spec <- log(spec + 1e-10)
  cepstrum <- Re(fft(log_spec, inverse = TRUE) / n)

  # 3. Define Quefrency axis (seconds) & Half Cepstrum
  quefrency <- (0:(n / 2 - 1)) / Fs
  cepstrum_half <- cepstrum[1:(n / 2)]

  # 4. Target Quefrency: Period of the Intermediate Shaft (Fault Location)
  target_quefrency <- 1 / intermediate_shaft_hz

  # 5. Find Amplitude in search window (+/- 10 samples for jitter)
  target_idx <- which.min(abs(quefrency - target_quefrency))

  # Handle edge case if target_idx is too close to start
  start_win <- max(1, target_idx - 10)
  end_win <- min(length(cepstrum_half), target_idx + 10)

  rahmonic_amp <- max(cepstrum_half[start_win:end_win])

  return(rahmonic_amp)
}

# ============================================================================
# HELPER 3: TSA RESIDUAL FM4 (Stage 2 Feature)
# ============================================================================
compute_tsa_fm4 <- function(signal_vec, keyphasor_edges, Fs) {
  # We perform TSA synchronous to the Input Shaft (Key Phasor).
  # The fault is on the Intermediate Shaft (Non-synchronous).
  # Therefore, the fault will appear in the RESIDUAL signal.

  num_revs <- length(keyphasor_edges) - 1
  if (num_revs < 1) {
    return(NA)
  }

  # Target points per revolution for resampling
  target_points <- 2048
  tsa_matrix <- matrix(0, nrow = num_revs, ncol = target_points)

  # 1. Angular Resampling
  for (i in 1:num_revs) {
    start_idx <- keyphasor_edges[i]
    end_idx <- keyphasor_edges[i + 1]

    segment <- signal_vec[start_idx:end_idx]

    # Linear interpolation to stretch/shrink to fixed length
    tsa_matrix[i, ] <- approx(
      x = seq_along(segment),
      y = segment,
      n = target_points
    )$y
  }

  # 2. Compute TSA (Mean) and Residual (Difference)
  tsa_mean <- colMeans(tsa_matrix, na.rm = TRUE)
  residual_matrix <- sweep(tsa_matrix, 2, tsa_mean, "-")

  # 3. FM4 (Kurtosis) of the Residual
  # Flatten the matrix to treat it as one continuous residual signal
  residual_signal <- as.vector(residual_matrix)
  fm4 <- kurtosis(residual_signal)

  return(fm4)
}

# ============================================================================
# MAIN PROCESSING FUNCTION (Handles Row-wise Structure)
# ============================================================================
process_gearbox_data <- function(
  folder_path,
  vib_channels = c(4, 5),
  keyphasor_channel = 7,
  indices_to_process = NULL # If NULL, process all rows
) {
  cat(paste("Loading data from:", basename(folder_path), "\n"))

  # 1. Load the Key Phasor File (Channel 7)
  # We assume the file name format is "channel_7.csv"
  kp_path <- file.path(
    folder_path,
    paste0("channel_", keyphasor_channel, ".csv")
  )
  if (!file.exists(kp_path)) {
    stop("Key Phasor file not found: ", kp_path)
  }

  # Read entire file (faster than row-by-row)
  # data.table::fread is very efficient for this size (~150MB)
  dt_kp <- fread(kp_path, header = TRUE)

  # Determine which rows to process
  if (is.null(indices_to_process)) {
    rows_to_run <- 1:nrow(dt_kp)
  } else {
    rows_to_run <- indices_to_process
  }

  # 2. Load Vibration Channels
  vib_data_list <- list()
  for (ch in vib_channels) {
    vib_path <- file.path(folder_path, paste0("channel_", ch, ".csv"))
    cat(paste("  Loading Channel", ch, "...\n"))
    vib_data_list[[as.character(ch)]] <- fread(vib_path, header = TRUE)
  }

  # 3. Process Rows
  cat("  Computing features...\n")
  results_list <- list()

  # We iterate through the requested row indices
  # Note: i is the actual row index in the CSV
  for (i in rows_to_run) {
    # Extract row as numeric vector
    # unlist ensures we get a vector, not a 1-row data.table
    kp_vec <- as.numeric(dt_kp[i, ])

    # Get Speed Info
    kp_info <- get_shaft_speed_from_keyphasor(kp_vec)

    if (is.na(kp_info$hz)) {
      # Handle cases where engine might be off or sensor bad
      next
    }

    # Initialize result row
    row_res <- list(Row_Index = i, Input_RPM = kp_info$hz * 60)

    # Compute features for each vibration channel
    for (ch in vib_channels) {
      # Extract vibration signal vector for this row
      sig_vec <- as.numeric(vib_data_list[[as.character(ch)]][i, ])

      # Stage 1: Cepstrum
      cep_amp <- compute_cepstrum_features(sig_vec, Fs = 12800, kp_info$hz)
      row_res[[paste0("Cepstrum_Ch", ch)]] <- cep_amp

      # Stage 2: TSA FM4
      fm4_val <- compute_tsa_fm4(sig_vec, kp_info$edges, Fs = 12800)
      row_res[[paste0("FM4_Ch", ch)]] <- fm4_val
    }

    results_list[[length(results_list) + 1]] <- as.data.frame(row_res)

    if (length(results_list) %% 100 == 0) {
      cat(paste("    Processed", length(results_list), "signals\n"))
    }
  }

  return(bind_rows(results_list))
}

# ============================================================================
# IMPROVED MATCHING LOGIC (Multivariate: Cepstrum + FM4)
# ============================================================================
find_matching_sequence <- function(test_df, train_df, top_n = 25) {
  window_size <- nrow(test_df)

  # --- 1. Select Feature Columns ---
  # We now use BOTH Cepstrum (Modulation) AND FM4 (Localized Faults)
  # This gives a holistic view of degradation.
  feature_cols <- grep("Cepstrum|FM4", names(test_df), value = TRUE)

  # --- 2. Normalize (Scale) Features ---
  # We must scale the Training data to have mean=0, sd=1.
  # Then we scale the Test data using the Training metrics (to keep reference).

  train_mat_raw <- as.matrix(train_df[, feature_cols])

  # Calculate Train stats
  train_means <- colMeans(train_mat_raw, na.rm = TRUE)
  train_sds <- apply(train_mat_raw, 2, sd, na.rm = TRUE)

  # Avoid division by zero for constant columns
  train_sds[train_sds == 0] <- 1

  # Scale Train
  train_mat_scaled <- scale(
    train_mat_raw,
    center = train_means,
    scale = train_sds
  )

  # Scale Test (using Train stats!)
  test_mat_raw <- as.matrix(test_df[, feature_cols])
  test_mat_scaled <- sweep(test_mat_raw, 2, train_means, "-")
  test_mat_scaled <- sweep(test_mat_scaled, 2, train_sds, "/")

  # --- 3. Run Sliding Window Matching (Correlation) ---
  n_train <- nrow(train_df)
  n_windows <- n_train - window_size + 1
  cor_scores <- numeric(n_windows)

  # Flatten Test matrix for vector comparison?
  # Actually, for multivariate matching, we often calculate the correlation
  # between the *vector of features* at each time step, or the correlation
  # of the flattened window.
  # Let's use the "Flattened Window" correlation: matching the exact shape
  # of the evolution of ALL features simultaneously.

  test_vec <- as.vector(test_mat_scaled)

  for (i in 1:n_windows) {
    # Extract window from scaled training data
    window_mat <- train_mat_scaled[i:(i + window_size - 1), ]
    train_vec <- as.vector(window_mat)

    # Compute Pearson Correlation
    # (Robust to amplitude scaling, sensitive to shape/pattern)
    cor_scores[i] <- cor(test_vec, train_vec)
  }

  # --- 4. Extract Top N Matches ---
  top_indices <- order(cor_scores, decreasing = TRUE)[
    1:min(top_n, length(cor_scores))
  ]

  top_matches_df <- data.frame(
    Rank = 1:length(top_indices),
    Start_Index_G1 = train_df$Row_Index[top_indices],
    Correlation = cor_scores[top_indices]
  )

  return(list(
    best_match = top_matches_df[1, ],
    top_matches = top_matches_df,
    all_scores = cor_scores
  ))
}
```


```{r}
# ============================================================================
# MEMORY-SAFE ENSEMBLE EXECUTION
# ============================================================================

library(dplyr)
library(data.table) # Ensure data.table is loaded for fread
library(plotly)

# 1. Configuration
base_path <- "C:/Users/shish/Documents/rul_challenge_data"
test_gearbox <- "G_6"
test_set <- "test_1"

# Channels: Radial (4,5) + Torque (8) + Keyphasor (7)
vib_channels <- c(4, 5, 8)
keyphasor_channel <- 7

# Training Gearboxes to process
train_gearboxes <- c("G_1", "G_2", "G_3", "G_4", "G_5")

# -----------------------------------------------------------------------------
# STEP 2: SEQUENTIAL FEATURE EXTRACTION (Process -> Save -> Clear Memory)
# -----------------------------------------------------------------------------

for (gb in train_gearboxes) {
  feature_file <- paste0(gb, "_spur_config_features.rds")

  if (file.exists(feature_file)) {
    cat(paste("Skipping", gb, "- Features already exist on disk.\n"))
  } else {
    cat(paste("\n=== Processing", gb, "to extract features ===\n"))

    # 1. Construct path
    gb_folder <- file.path(base_path, "train", gb)

    # 2. Run Processing (Loads ~2GB RAM peak for this gearbox only)
    # NOTE: Ensure process_gearbox_data is defined in your environment
    feats <- process_gearbox_data(
      folder_path = gb_folder,
      vib_channels = vib_channels,
      keyphasor_channel = keyphasor_channel
    )

    # 3. Save to disk immediately
    saveRDS(feats, feature_file)
    cat(paste("Saved features to", feature_file, "\n"))

    # 4. CRITICAL: Clear Memory
    rm(feats) # Remove the dataframe
    gc() # Force Garbage Collection to free RAM before next iteration
    cat("Memory cleared.\n")
  }
}

# -----------------------------------------------------------------------------
# STEP 3: PROCESS TEST DATA (G_6)
# -----------------------------------------------------------------------------
cat("\n=== Processing Test Data (G_6) ===\n")
test_folder <- file.path(base_path, "test", test_gearbox, test_set)

# We don't cache test data usually as it's small (5 rows), but good practice to be consistent
test_features <- process_gearbox_data(
  folder_path = test_folder,
  vib_channels = vib_channels,
  keyphasor_channel = keyphasor_channel,
  indices_to_process = 1:5
)

# -----------------------------------------------------------------------------
# STEP 4: ENSEMBLE MATCHING (Loads only lightweight features)
# -----------------------------------------------------------------------------
ensemble_results <- data.frame()

cat("\n=== STARTING ENSEMBLE MATCHING ===\n")

for (gb in train_gearboxes) {
  # Load ONLY the features (Tiny file, negligible memory)
  feature_file <- paste0(gb, "_spur_config_features.rds")
  train_df <- readRDS(feature_file)

  # Run matching logic
  # Using Top 25 to assess spread/correlation
  match_res <- find_matching_sequence(test_features, train_df, top_n = 25)

  # Calculate Correlation Score (Shape matching)
  # We re-calculate correlation for the best match window found by Cosine Similarity
  # or scan for best correlation directly.

  # Let's find the index with the highest Correlation Score among the available windows
  cols_to_use <- grep("Cepstrum", names(test_features), value = TRUE)
  test_mat <- as.matrix(test_features[, cols_to_use])
  train_mat <- as.matrix(train_df[, cols_to_use])

  n_windows <- nrow(train_df) - nrow(test_features) + 1
  cor_scores <- numeric(n_windows)

  # Fast correlation loop
  for (i in 1:n_windows) {
    window_mat <- train_mat[i:(i + nrow(test_features) - 1), ]
    # Mean correlation across features
    cors <- numeric(ncol(test_mat))
    for (j in 1:ncol(test_mat)) {
      cors[j] <- cor(test_mat[, j], window_mat[, j])
    }
    cor_scores[i] <- mean(cors, na.rm = TRUE)
  }

  best_idx <- which.max(cor_scores)
  max_cor <- max(cor_scores, na.rm = TRUE)

  # Calculate % Life
  life_pct <- (best_idx / nrow(train_df)) * 100

  # Store Result
  ensemble_results <- rbind(
    ensemble_results,
    data.frame(
      Train_Gearbox = gb,
      Load_Condition = ifelse(
        gb %in% c("G_1", "G_2", "G_3"),
        "Low (17.9Nm)",
        "High (26.5Nm)"
      ),
      Best_Start_Index = best_idx,
      Total_Life_Cycles = nrow(train_df),
      Life_Percentage = life_pct,
      Max_Correlation = max_cor
    )
  )

  # Clean up loop variables
  rm(train_df, train_mat, cor_scores)
}

# -----------------------------------------------------------------------------
# STEP 5: ANALYZE & VISUALIZE
# -----------------------------------------------------------------------------
print(ensemble_results)

# Weighted Average (Weight by Correlation Score)
# Higher correlation = Better shape match = More trust in that result
weighted_life <- sum(
  ensemble_results$Life_Percentage * ensemble_results$Max_Correlation
) /
  sum(ensemble_results$Max_Correlation)

cat(sprintf("\n=== ENSEMBLE PREDICTION ===\n"))
cat(sprintf("Weighted Average Degradation: %.2f%%\n", weighted_life))

# Visualization
fig <- plot_ly(
  ensemble_results,
  x = ~Train_Gearbox,
  y = ~Life_Percentage,
  type = 'bar',
  color = ~Load_Condition,
  text = ~ paste0(round(Life_Percentage, 1), "%"),
  textposition = 'auto',
  marker = list(line = list(width = 1.5))
) %>%
  layout(
    title = "Estimated Degradation Stage by Training Gearbox",
    yaxis = list(title = "Estimated Life Percentage (%)", range = c(0, 100)),
    xaxis = list(title = "Training Reference")
  )

fig
```
