---
title: "Visualizations and Analysis"
format: html
---

```{r}

# renv::install("signal")
# renv::install("e1071")
# renv::install("av")

library(tidyverse)
library(DBI)
library(duckdb)
library(sparklyr)
library(signal)
library(e1071)
library(av)
```

Connect to DuckDB

```{r}
# Connect to the DuckDB database (or create it if it doesn't exist)
con <- dbConnect(
  duckdb::duckdb(),
  "C:\\Users\\shish\\Documents\\rul_challenge_data\\DuckDB\\large_data_warehouse.duckdb"
)
```

Connect and load the first table

```{r}
# Lazy table connection to G_1.channel_1

g1_channel1_lazy <- tbl(con, "G_1.channel_1")

g1_channel1_lazy_df <- g1_channel1_lazy %>%
  collect()

```

For every row (i.e. signal), compute the spectral kurtosis using differnt window sizes.

```{r}

start_time <- Sys.time()

# Generate row indices for all rows in the data frame
row_indices <- seq(1, nrow(g1_channel1_lazy_df), by = 1)

# Initialize list to store plots
plot_list <- list()

# Initialize list to store results_list from each signal
all_signals_results <- list()

# Loop through each selected row index
for (idx in seq_along(row_indices)) {
  row_num <- row_indices[idx]

  # Pull signal from the selected row
  final_signal <- g1_channel1_lazy_df[row_num, ]

  # Extract signal vector
  x <- final_signal[1, ] |> unlist() |> as.numeric()

  # Set parameters
  Fs <- 12800
  window_lengths <- c(16, 32, 64, 128, 256)
  results_list <- list()

  # Compute spectral kurtosis for different window lengths
  for (w_len in window_lengths) {
    o_len <- 0.8 * w_len

    spec_output <- specgram(
      x,
      n = 1024,
      Fs = Fs,
      overlap = o_len,
      window = hanning(w_len)
    )
    P_matrix <- Mod(spec_output$S)^2
    freq_bins <- spec_output$f

    # Exclude DC bin
    P_data <- P_matrix[-c(1), ]
    freq_data <- freq_bins[-c(1)]

    num_freq_bins <- nrow(P_data)
    sk_values <- numeric(num_freq_bins)

    for (i in 1:num_freq_bins) {
      energy_envelope <- P_data[i, ]
      sk_values[i] <- e1071::kurtosis(energy_envelope, type = 1) + 1
    }

    # Calculate area under the SK curve using base R
    # 1. Calculate the average height of each trapezoid: (y_i + y_{i+1}) / 2
    average_heights <- (sk_values[-length(sk_values)] + sk_values[-1]) / 2

    # 2. Calculate the width of each trapezoid: (x_{i+1} - x_i)
    # diff(freq_data) calculates the difference between consecutive elements
    widths <- diff(freq_data)

    # 3. Sum the areas (height * width)
    area_under_sk_base_r <- sum(average_heights * widths)

    results_list[[as.character(w_len)]] <- data.frame(
      Frequency_kHz = freq_data / 1000,
      SK = sk_values,
      Window_Size = as.factor(w_len),
      Area_Under_SK = area_under_sk_base_r
    )
  }

  # Combine results
  plotting_df <- do.call(rbind, results_list)

  # Create plot
  p <- ggplot(
    plotting_df,
    aes(x = Frequency_kHz, y = SK, color = Window_Size)
  ) +
    geom_line(linewidth = 1) +
    labs(
      title = paste0("Spectral Kurtosis - Signal Row ", row_num),
      x = "Frequency [kHz]",
      y = "Spectral Kurtosis",
      color = "Window Length (Nw)"
    ) +
    scale_x_continuous(limits = c(0, Fs / 2000)) +
    scale_y_continuous(limits = c(0, 70)) +
    theme_minimal() +
    theme(legend.position = "right")

  # Store plot in list
  plot_list[[idx]] <- p

  # Store results_list in all_signals_results
  all_signals_results[[idx]] <- plotting_df

  #cat("Processed signal", idx, "of 10 (row", row_num, ")\n")

  cat(
    "Processed signal",
    idx,
    "of",
    length(row_indices),
    "(row",
    row_num,
    ")\n"
  )
}

end_time <- Sys.time()
time_taken <- end_time - start_time
cat("Total time taken:", time_taken, "\n")

```

Save all_signals_results for future analysis

```{r}
# Save plot_list and all_signals_results for future analysis

# saveRDS(plot_list, "spectral_kurtosis_plots_list.rds")
saveRDS(
  all_signals_results,
  "G1_channel1_spectral_kurtosis_all_signals_results.rds"
)
```

Create a video of the plots in plot_list

```{r}
library(av)

# Create temporary directory
temp_dir <- "temp_plots"
dir.create(temp_dir, showWarnings = FALSE)

# Save plots as temporary images
for (i in seq_along(plot_list)) {
  temp_file <- file.path(temp_dir, sprintf("plot_%04d.png", i))
  ggsave(temp_file, plot = plot_list[[i]], width = 10, height = 7, dpi = 100)

  if (i %% 100 == 0) cat("Processing", i, "of", length(plot_list), "plots\n")
}

# Create video from images
av_encode_video(
  input = list.files(temp_dir, pattern = "plot_.*\\.png", full.names = TRUE),
  output = "spectral_kurtosis_video.mp4",
  framerate = 10, # 10 frames per second
  vfilter = "format=yuv420p" # Better compatibility
)

# Clean up
unlink(temp_dir, recursive = TRUE)


```

Load all_signals_results for analysis. Then, I want to plot area under spectral kurtosis against signal index for all window sizes.


```{r}
G1_channel1_spectral_kurtosis_all_signals_results <- readRDS(
  "G1_channel2_spectral_kurtosis_all_signals_results.rds"
)

# plot area under spectral kurtosis against signal index for all window sizes.
# Combine area under SK data for all signals
area_data <- data.frame()
for (i in seq_along(G1_channel1_spectral_kurtosis_all_signals_results)) {
  signal_df <- G1_channel1_spectral_kurtosis_all_signals_results[[i]]

  # Extract unique area under SK values for each window size
  area_values <- signal_df %>%
    select(Window_Size, Area_Under_SK) %>%
    distinct()

  area_values$Signal_Index <- i

  area_data <- rbind(area_data, area_values)
}

area_data_filtered <- area_data %>%
  dplyr::filter(Window_Size %in% c("32"))

# Plot area under SK vs Signal Index for all window sizes
p_area <- ggplot(
  area_data_filtered,
  aes(x = Signal_Index, y = Area_Under_SK, color = Window_Size)
) +
  geom_line() +
  labs(
    title = "Area Under Spectral Kurtosis vs Signal Index",
    x = "Signal Index",
    y = "Area Under Spectral Kurtosis",
    color = "Window Length (Nw)"
  ) +
  theme_minimal() +
  theme(legend.position = "right")

p_area
```

Write a function that takes in a channel, calculates the following, and stores them in a data frame:

1. Time domain features (mean, std, peak to peak, rms, skewness, kurtosis, crest factor, shape factor, impulse factor, margin factor, energy) for every row in the channel and stores it in a list. Each list element contains the time domain features for one signal (row).
2. Calculate the spectral kurtosis for every row in the channel using different window sizes (16, 32, 64, 128, 256) and stores them in a list. Each list element contains a data frame with frequency, spectral kurtosis values, window size for one signal (row).
3. Create a new list where each element contains a dataframe with columns as window size, mean spectral kurtosis, std. dev spectral kurtosis, kurtosis-spectral kurtosis, skewness-spectral kurtosis, peak-to-peak spectral kurtosis and area under curve spectral kurtosis. This data frame is built based on the data in point 2 above. Note that only the frequencies between 500 Hz and 5500 Hz from the data frames in point 2 above must be used. Each list element is for one signal (row)


```{r}

calculate_vibration_timeDomainFeatures <- function(signal_vector) {
  # --- Intermediate Calculations ---
  abs_signal <- abs(signal_vector)

  # Peak Value (Maximum Absolute Amplitude, xp)
  peak_value <- max(abs_signal)

  # RMS: Root Mean Square
  rms_value <- sqrt(mean(signal_vector^2))

  # Absolute Mean (Mean of the absolute values, or Rectified Mean)
  abs_mean <- mean(abs_signal)

  # Denominator for Margin Factor
  # Formula: ( 1/N * sum(|x_i|) )^2
  margin_denominator <- (abs_mean)^2

  # --- Feature Calculations ---
  results <- list(
    # Basic Stats
    Mean = mean(signal_vector),
    Std_Dev = sd(signal_vector),
    Peak_to_Peak = max(signal_vector) - min(signal_vector),
    RMS = rms_value,

    # Statistical Moments
    Skewness = skewness(signal_vector),
    Kurtosis = kurtosis(signal_vector),

    # Factors (using the robust peak_value = max(|x|))
    Crest_Factor = peak_value / rms_value,
    Shape_Factor = rms_value / abs_mean,
    Impulse_Factor = peak_value / abs_mean,

    # Margin Factor (Denominator: Squared Mean of the Absolute Values)
    Margin_Factor = peak_value / margin_denominator,

    # Energy
    Energy = sum(signal_vector^2) # Sum of Squares
  )

  return(results)
}


process_channel_features <- function(channel_data, Fs = 12800) {
  # Initialize output lists
  time_domain_features_list <- list()
  spectral_kurtosis_list <- list()
  sk_summary_features_list <- list()

  # Get number of signals (rows)
  n_signals <- nrow(channel_data)

  # Process each signal
  for (row_idx in 1:n_signals) {
    # --- 1. Extract signal ---
    signal_vector <- channel_data[row_idx, ] |> unlist() |> as.numeric()

    # --- 2. Calculate Time Domain Features ---
    time_features <- calculate_vibration_timeDomainFeatures(signal_vector)
    time_domain_features_list[[row_idx]] <- as.data.frame(time_features)

    # --- 3. Calculate Spectral Kurtosis ---
    window_lengths <- c(16, 32, 64, 128, 256)
    results_list <- list()

    for (w_len in window_lengths) {
      o_len <- 0.8 * w_len

      # Compute spectrogram
      spec_output <- specgram(
        signal_vector,
        n = 1024,
        Fs = Fs,
        overlap = o_len,
        window = hanning(w_len)
      )

      P_matrix <- Mod(spec_output$S)^2
      freq_bins <- spec_output$f

      # Exclude DC bin
      P_data <- P_matrix[-1, ]
      freq_data <- freq_bins[-1]

      # Calculate SK for each frequency bin
      num_freq_bins <- nrow(P_data)
      sk_values <- numeric(num_freq_bins)

      for (i in 1:num_freq_bins) {
        energy_envelope <- P_data[i, ]
        sk_values[i] <- e1071::kurtosis(energy_envelope, type = 1) + 1
      }

      # Store SK results
      results_list[[as.character(w_len)]] <- data.frame(
        Frequency_Hz = freq_data,
        SK = sk_values,
        Window_Size = as.factor(w_len)
      )
    }

    # Combine all window sizes for this signal
    spectral_kurtosis_list[[row_idx]] <- do.call(rbind, results_list)

    # --- 4. Calculate SK Summary Features (500-5500 Hz) ---
    sk_summary_df <- data.frame()

    for (w_len in window_lengths) {
      # Filter data for this window size and frequency range
      sk_data <- results_list[[as.character(w_len)]] |>
        dplyr::filter(Frequency_Hz >= 500 & Frequency_Hz <= 5500)

      # Extract SK values in the frequency range
      sk_vals <- sk_data$SK
      freq_vals <- sk_data$Frequency_Hz

      # Calculate area under curve using trapezoidal rule
      average_heights <- (sk_vals[-length(sk_vals)] + sk_vals[-1]) / 2
      widths <- diff(freq_vals)
      area_under_curve <- sum(average_heights * widths)

      # Calculate summary statistics
      summary_row <- data.frame(
        Window_Size = w_len,
        Mean_SK = mean(sk_vals, na.rm = TRUE),
        StdDev_SK = sd(sk_vals, na.rm = TRUE),
        Kurtosis_SK = e1071::kurtosis(sk_vals),
        Skewness_SK = e1071::skewness(sk_vals),
        PeakToPeak_SK = max(sk_vals, na.rm = TRUE) - min(sk_vals, na.rm = TRUE),
        AUC_SK = area_under_curve
      )

      sk_summary_df <- rbind(sk_summary_df, summary_row)
    }

    sk_summary_features_list[[row_idx]] <- sk_summary_df

    # Progress indicator
    if (row_idx %% 100 == 0) {
      cat("Processed signal", row_idx, "of", n_signals, "\n")
    }
  }

  # Return all three lists
  return(list(
    time_domain_features = time_domain_features_list,
    spectral_kurtosis = spectral_kurtosis_list,
    sk_summary_features = sk_summary_features_list
  ))
}
```

Loop through all channels

```{r}
# Define schemas and channels
schemas <- c("G_1", "G_2", "G_3", "G_4", "G_5")
channels <- c(
  "channel_1",
  "channel_2",
  "channel_3",
  "channel_4",
  "channel_5",
  "channel_6",
  "channel_11"
)

# Get list of all available tables in the database
all_tables <- dbListTables(con)

# Process each schema
for (schema in schemas) {
  cat("\n=== Processing Schema:", schema, "===\n")

  # Process each channel
  for (channel in channels) {
    table_name <- paste0(schema, ".", channel)

    # Check if table exists
    if (!table_name %in% all_tables) {
      cat("Table", table_name, "does not exist. Skipping.\n")
      next
    }

    cat("\nProcessing:", table_name, "\n")

    # Create output directory structure
    output_dir <- file.path(schema, channel)
    dir.create(output_dir, recursive = TRUE, showWarnings = FALSE)

    # Connect to the channel lazily
    channel_lazy <- tbl(con, table_name)

    # Collect data into memory
    channel_data <- channel_lazy |> collect()

    cat("Loaded", nrow(channel_data), "signals from", table_name, "\n")

    # Process the channel
    start_time <- Sys.time()
    results <- process_channel_features(channel_data, Fs = 12800)
    end_time <- Sys.time()

    cat(
      "Processing completed in",
      round(difftime(end_time, start_time, units = "mins"), 2),
      "minutes\n"
    )

    # Save results
    saveRDS(
      results$time_domain_features,
      file.path(output_dir, "time_domain_features.rds")
    )

    saveRDS(
      results$spectral_kurtosis,
      file.path(output_dir, "spectral_kurtosis.rds")
    )

    saveRDS(
      results$sk_summary_features,
      file.path(output_dir, "sk_summary_features.rds")
    )

    cat("Results saved to:", output_dir, "\n")

    # Clear channel data from memory
    rm(channel_data, channel_lazy, results)
    gc() # Force garbage collection

    cat("Memory cleared for next channel\n")
  }
}

cat("\n=== All channels processed successfully ===\n")
```


##

```{r}
g1_channel1_lazy <- tbl(con, "G_1.channel_1")

# Last row index

last_row_index <- g1_channel1_lazy %>%
  summarise(row_count = n()) %>%
  collect() %>%
  pull(row_count)

# Pull last row from the table
final_signal <- g1_channel1_lazy %>%
  dplyr::filter(row_number() == last_row_index) %>%
  collect()

# store "x" as a vector for analysis

x <- final_signal[1, ] %>% unlist() %>% as.numeric()


# Replication of Figure 19(b) using ggplot2 in R
# --- 1. Define Parameters and Data ---

Fs <- 12800 # Sampling Frequency (Hz)
N <- length(final_signal) # Total Length of signal (32768 samples)

# # Simulated Signal: Stationary noise + Non-stationary impulses (fault)
# t <- (1:N) / Fs
# x <- sin(2 * pi * 100 * t) + 0.1 * rnorm(N)
# # Add sharp impulses repeating at 50 Hz
# impulse_indices <- seq(1, N, by = round(Fs / 50))
# x[impulse_indices] <- x[impulse_indices] + 5
# x <- as.numeric(x)

# Window lengths to test (from Figure 19b)
window_lengths <- c(16, 32, 64, 128, 256)

# Data structure to hold all SK results
results_list <- list()

# --- 2. Loop Through Different Window Lengths and Compute SK ---

for (w_len in window_lengths) {
  # Set overlap to half the window length (standard practice)
  o_len <- 0.8 * w_len

  # Compute Spectrogram: spec_output$S is the complex spectral estimate
  spec_output <- specgram(
    x,
    n = 1024,
    Fs = Fs,
    overlap = o_len,
    window = hanning(w_len)
  )

  # Calculate REAL-VALUED POWER (P = |S|^2)
  P_matrix <- Mod(spec_output$S)^2

  # Get frequency bins
  freq_bins <- spec_output$f

  # Data Cleaning (Exclude DC). Nyquist is already excluded by specgram function.
  P_data <- P_matrix[-c(1), ]
  freq_data <- freq_bins[-c(1)]

  num_freq_bins <- nrow(P_data)
  sk_values <- numeric(num_freq_bins)

  # Compute Spectral Kurtosis for Each Single Frequency Bin
  for (i in 1:num_freq_bins) {
    energy_envelope <- P_data[i, ]
    sk_values[i] <- e1071::kurtosis(energy_envelope, type = 1) + 1 # The +1 is to match spectral kurtosis definition in the literature.
  }

  # Store results in a data frame, including the window size as a factor
  results_list[[as.character(w_len)]] <- data.frame(
    Frequency_kHz = freq_data / 1000,
    SK = sk_values,
    Window_Size = as.factor(w_len)
  )
}

# --- 3. Plotting the Results using ggplot2 ---

# Combine all data frames into one long data frame
plotting_df <- do.call(rbind, results_list)

# Generate the ggplot object
p <- ggplot(plotting_df, aes(x = Frequency_kHz, y = SK, color = Window_Size)) +
  geom_line(linewidth = 1) +
  labs(
    title = "Replication of Figure 19(b) (SK vs. Frequency)",
    x = "Frequency [kHz]",
    y = "Spectral Kurtosis",
    color = "Window Length (Nw)"
  ) +
  # Set limits similar to the original figure (0 to Nyquist, or 5 kHz)
  scale_x_continuous(limits = c(0, Fs / 2000)) +
  scale_y_continuous(limits = c(0, 70)) +
  theme_minimal() +
  theme(legend.position = "right")

p

# Save the plot
ggsave("G_1_Channel_1_FirstRow.png", p, width = 10, height = 7)
```

Now, do the same thing above, but in a loop.

```{r}
# Get the last row index
last_row_index <- g1_channel1_lazy |>
  summarise(row_count = n()) |>
  collect() |>
  pull(row_count)

# Generate 10 equally spaced row indices from first to last
row_indices <- round(seq(1, last_row_index, length.out = 10))

# Initialize list to store plots
plot_list <- list()

# Loop through each selected row index
for (idx in seq_along(row_indices)) {
  row_num <- row_indices[idx]

  # Pull signal from the selected row
  final_signal <- g1_channel1_lazy |>
    dplyr::filter(row_number() == row_num) |>
    collect()

  # Extract signal vector
  x <- final_signal[1, ] |> unlist() |> as.numeric()

  # Set parameters
  Fs <- 12800
  window_lengths <- c(16, 32, 64, 128, 256)
  results_list <- list()

  # Compute spectral kurtosis for different window lengths
  for (w_len in window_lengths) {
    o_len <- 0.8 * w_len

    spec_output <- specgram(
      x,
      n = 1024,
      Fs = Fs,
      overlap = o_len,
      window = hanning(w_len)
    )
    P_matrix <- Mod(spec_output$S)^2
    freq_bins <- spec_output$f

    # Exclude DC bin
    P_data <- P_matrix[-c(1), ]
    freq_data <- freq_bins[-c(1)]

    num_freq_bins <- nrow(P_data)
    sk_values <- numeric(num_freq_bins)

    for (i in 1:num_freq_bins) {
      energy_envelope <- P_data[i, ]
      sk_values[i] <- e1071::kurtosis(energy_envelope, type = 1) + 1
    }

    results_list[[as.character(w_len)]] <- data.frame(
      Frequency_kHz = freq_data / 1000,
      SK = sk_values,
      Window_Size = as.factor(w_len)
    )
  }

  # Combine results
  plotting_df <- do.call(rbind, results_list)

  # Create plot
  p <- ggplot(
    plotting_df,
    aes(x = Frequency_kHz, y = SK, color = Window_Size)
  ) +
    geom_line(linewidth = 1) +
    labs(
      title = paste0("Spectral Kurtosis - Signal Row ", row_num),
      x = "Frequency [kHz]",
      y = "Spectral Kurtosis",
      color = "Window Length (Nw)"
    ) +
    scale_x_continuous(limits = c(0, Fs / 2000)) +
    scale_y_continuous(limits = c(0, 70)) +
    theme_minimal() +
    theme(legend.position = "right")

  # Store plot in list
  plot_list[[idx]] <- p

  cat("Processed signal", idx, "of 10 (row", row_num, ")\n")
}

# Now you can view individual plots
# plot_list[[1]]  # First signal
# plot_list[[10]] # Last signal
```


Function to extract the time domain features

```{r}

calculate_vibration_timeDomainFeatures <- function(signal_vector) {
  # --- Intermediate Calculations ---
  abs_signal <- abs(signal_vector)

  # Peak Value (Maximum Absolute Amplitude, xp)
  peak_value <- max(abs_signal)

  # RMS: Root Mean Square
  rms_value <- sqrt(mean(signal_vector^2))

  # Absolute Mean (Mean of the absolute values, or Rectified Mean)
  abs_mean <- mean(abs_signal)

  # Denominator for Margin Factor
  # Formula: ( 1/N * sum(|x_i|) )^2
  margin_denominator <- (abs_mean)^2

  # --- Feature Calculations ---
  results <- list(
    # Basic Stats
    Mean = mean(signal_vector),
    Std_Dev = sd(signal_vector),
    Peak_to_Peak = max(signal_vector) - min(signal_vector),
    RMS = rms_value,

    # Statistical Moments
    Skewness = skewness(signal_vector),
    Kurtosis = kurtosis(signal_vector),

    # Factors (using the robust peak_value = max(|x|))
    Crest_Factor = peak_value / rms_value,
    Shape_Factor = rms_value / abs_mean,
    Impulse_Factor = peak_value / abs_mean,

    # Margin Factor (Denominator: Squared Mean of the Absolute Values)
    Margin_Factor = peak_value / margin_denominator,

    # Energy
    Energy = sum(signal_vector^2) # Sum of Squares
  )

  return(results)
}
```