---
title: "Untitled"
format: html
---

This document is used to plot power(dB) vs frequency, Power (RMS) vs frequency and spectral kurtosis vs frequency   graph for 5 different window sizes (32, 64, 128, 256, 512). I want 80% overlap. For a given channel, I will plot every 30th signal. This will give me an idea about the dominant frequencies present in the signal for different window sizes. Once you have this plot, take a decision on the window size to be used for further analysis. Please give me the code. Like before, I want to visualize the different window sizes in the same plot for comparison. Also, like before, I want a plotly plot where each frame is a signal. I want a function that takes in a channel and outputs a plotly plot. Please give me the code. 

```{r}

# renv::install("signal")
# renv::install("e1071")
# renv::install("av")
# renv::install("future")
# renv::install("furrr")
# renv::install("plotly")
# renv::install("htmlwidgets")
# renv::install("pracma")

library(tidyverse)
library(DBI)
library(duckdb)
library(sparklyr)
library(signal)
library(e1071)
library(av)
library(parallel)
library(future)
library(furrr)
library(data.table)
library(plotly)
library(htmlwidgets)
library(pracma)
```


FULL Code ::

```{r}
# ============================================================================
# PREPROCESSING FUNCTIONS
# ============================================================================

preprocess_signal <- function(signal_vector, Fs = 12800) {
  # Step 1: Detrending - Remove the mean
  detrended_signal <- signal_vector - mean(signal_vector)

  # Step 2: Low-pass filtering
  nyquist_freq <- Fs / 2
  cutoff_freq <- 1 * nyquist_freq
  W <- cutoff_freq / nyquist_freq

  # Design Butterworth filter (4th order)
  butter_filter <- butter(n = 4, W = W, type = "low")

  # Apply the filter
  filtered_signal <- filtfilt(butter_filter, detrended_signal)

  return(filtered_signal)
}

calculate_vibration_timeDomainFeatures <- function(signal_vector) {
  abs_signal <- abs(signal_vector)
  peak_value <- max(abs_signal)
  rms_value <- sqrt(mean(signal_vector^2))
  abs_mean <- mean(abs_signal)
  margin_denominator <- (abs_mean)^2

  results <- list(
    Mean = mean(signal_vector),
    Std_Dev = sd(signal_vector),
    Peak_to_Peak = max(signal_vector) - min(signal_vector),
    RMS = rms_value,
    Skewness = skewness(signal_vector),
    Kurtosis = kurtosis(signal_vector),
    Crest_Factor = peak_value / rms_value,
    Shape_Factor = rms_value / abs_mean,
    Impulse_Factor = peak_value / abs_mean,
    Margin_Factor = peak_value / margin_denominator,
    Energy = sum(signal_vector^2)
  )

  return(results)
}

# ============================================================================
# STAGE 1: FAST SPECTRAL FINGERPRINTING (GMF-BASED) - MEMORY OPTIMIZED
# ============================================================================

extract_spectral_fingerprint <- function(
  signal,
  Fs = 12800,
  preprocess = TRUE,
  freq_min = 10,
  freq_max = 6400,
  gearbox_group = "G_1_to_G_3"
) {
  if (preprocess) {
    signal <- preprocess_signal(signal)
  }

  # Compute FFT
  n <- length(signal)
  fft_result <- fft(signal)
  magnitude <- Mod(fft_result[1:(n / 2)])
  freqs <- (0:(n / 2 - 1)) * Fs / n

  # Use full frequency range (exclude only DC and very low freq)
  freq_mask <- freqs >= freq_min & freqs <= freq_max
  magnitude_filtered <- magnitude[freq_mask]
  freqs_filtered <- freqs[freq_mask]

  # Define gear mesh frequencies
  GMF1 <- 1160      # Test gearbox: Input-Intermediate mesh
  GMF2 <- 439.6     # Test gearbox: Intermediate-Output mesh (PINION - FAILURE LOCATION)
  
  # Extract energy at GMF harmonics
  extract_gmf_harmonics <- function(gmf, n_harmonics = 5, bandwidth = 50) {
    harmonic_energies <- numeric(n_harmonics)
    for (h in 1:n_harmonics) {
      freq_center <- gmf * h
      freq_range <- (freqs_filtered >= (freq_center - bandwidth)) & 
                    (freqs_filtered <= (freq_center + bandwidth))
      if (sum(freq_range) > 0) {
        harmonic_energies[h] <- sum(magnitude_filtered[freq_range]^2)
      } else {
        harmonic_energies[h] <- 0
      }
    }
    return(harmonic_energies)
  }
  
  # Extract GMF harmonics
  gmf1_harmonics <- extract_gmf_harmonics(GMF1, n_harmonics = 3)
  gmf2_harmonics <- extract_gmf_harmonics(GMF2, n_harmonics = 5)

  # Standard spectral features
  total_energy <- sum(magnitude_filtered^2)
  
  spectral_centroid <- sum(freqs_filtered * magnitude_filtered) /
    sum(magnitude_filtered)

  spectral_spread <- sqrt(
    sum(((freqs_filtered - spectral_centroid)^2) * magnitude_filtered) /
      sum(magnitude_filtered)
  )

  cumsum_energy <- cumsum(magnitude_filtered^2)
  rolloff_idx <- which(cumsum_energy >= 0.85 * total_energy)[1]
  spectral_rolloff <- freqs_filtered[rolloff_idx]

  rms <- sqrt(mean(signal^2))
  
  # High frequency energy ratio
  high_freq_mask <- freqs_filtered >= 3000
  high_freq_energy_ratio <- sum(magnitude_filtered[high_freq_mask]^2) / total_energy

  return(c(
    Spectral_Centroid = spectral_centroid,
    Spectral_Spread = spectral_spread,
    Spectral_Rolloff = spectral_rolloff,
    RMS = rms,
    High_Freq_Energy_Ratio = high_freq_energy_ratio,
    GMF2_H1 = gmf2_harmonics[1],
    GMF2_H2 = gmf2_harmonics[2],
    GMF2_H3 = gmf2_harmonics[3],
    GMF2_H4 = gmf2_harmonics[4],
    GMF2_H5 = gmf2_harmonics[5],
    GMF1_H1 = gmf1_harmonics[1],
    GMF1_H2 = gmf1_harmonics[2],
    GMF1_H3 = gmf1_harmonics[3]
  ))
}

precompute_spectral_fingerprints <- function(
  gearbox_path,
  channels = c(4, 5, 9),
  gearbox_name = "Gearbox",
  gearbox_group = NULL
) {
  cat("=== Computing spectral fingerprints for", gearbox_name, "===\n")
  
  # Auto-detect gearbox group
  if (is.null(gearbox_group)) {
    if (grepl("G_[123]", gearbox_path)) {
      gearbox_group <- "G_1_to_G_3"
    } else if (grepl("G_[456]", gearbox_path)) {
      gearbox_group <- "G_4_to_G_6"
    } else {
      warning("Could not detect gearbox group, defaulting to G_1_to_G_3")
      gearbox_group <- "G_1_to_G_3"
    }
  }
  
  cat("Detected gearbox group:", gearbox_group, "\n")

  # Get number of signals by reading only the first channel's row count
  channel_1_path <- file.path(gearbox_path, paste0("channel_", channels[1], ".csv"))
  n_signals <- nrow(fread(channel_1_path, select = 1L, header = TRUE))  # Only read first column to count rows
  
  cat("Total signals:", n_signals, "\n")

  # Initialize matrix
  fingerprints_matrix <- matrix(nrow = n_signals, ncol = 13)
  colnames(fingerprints_matrix) <- c(
    "Spectral_Centroid", "Spectral_Spread", "Spectral_Rolloff", 
    "RMS", "High_Freq_Energy_Ratio",
    "GMF2_H1", "GMF2_H2", "GMF2_H3", "GMF2_H4", "GMF2_H5",
    "GMF1_H1", "GMF1_H2", "GMF1_H3"
  )

  # Process each signal
  for (signal_idx in 1:n_signals) {
    # Average fingerprint across selected channels
    channel_fingerprints <- matrix(nrow = length(channels), ncol = 13)

    for (i in seq_along(channels)) {
      ch <- channels[i]
      channel_path <- file.path(gearbox_path, paste0("channel_", ch, ".csv"))
      
      # Read ONLY this one signal (one row) - MEMORY OPTIMIZED!
      signal <- fread(
        channel_path,
        skip = signal_idx - 1,  # Skip to the specific row
        nrows = 1,          # Read only 1 row
        header = TRUE      
      ) |> 
        unlist() |> 
        as.numeric()
      
      channel_fingerprints[i, ] <- extract_spectral_fingerprint(
        signal,
        gearbox_group = gearbox_group
      )
    }

    # Average across channels
    fingerprints_matrix[signal_idx, ] <- colMeans(
      channel_fingerprints,
      na.rm = TRUE
    )

    # Progress every 10 signals
    if (signal_idx %% 10 == 0) {
      cat("  Processed", signal_idx, "of", n_signals, "\n")
    }
  }

  rownames(fingerprints_matrix) <- paste0("Signal_", 1:n_signals)
  cat("Fingerprint extraction complete!\n\n")

  return(fingerprints_matrix)
}

compute_fingerprint_similarity <- function(
  test_fingerprints,
  train_fingerprints
) {
  # Normalize both
  test_norm <- scale(test_fingerprints)
  train_norm <- scale(train_fingerprints)

  # Flatten and compute cosine similarity
  test_vec <- as.vector(t(test_norm))
  train_vec <- as.vector(t(train_norm))

  # Remove NAs
  valid_idx <- !is.na(test_vec) & !is.na(train_vec)

  cosine_sim <- sum(test_vec[valid_idx] * train_vec[valid_idx]) /
    (sqrt(sum(test_vec[valid_idx]^2)) * sqrt(sum(train_vec[valid_idx]^2)))

  return(cosine_sim)
}

fast_candidate_selection_optimized <- function(
  test_gearbox_path,
  train_gearbox_path,
  test_signal_indices = 1:5,
  top_n_candidates = 50,
  fingerprint_channels = c(4, 5, 9),
  full_feature_channels = 1:11,
  test_gearbox = NULL,      # Add this
  test_set = NULL,          # Add this
  train_gearbox = NULL      # Add this
) {
  cat("=== Stage 1: Fast Spectral Fingerprint Screening ===\n")
  cat("Using channels:", paste(fingerprint_channels, collapse = ", "), 
      "(Output shaft vibrations + Acoustic emission)\n")
  cat("Focusing on pinion failure signatures (GMF harmonics)\n\n")

    # Create cache file names
  test_cache_file <- paste0(
    "fingerprints_",
    test_gearbox,
    "_",
    test_set,
    "_ch",
    paste(fingerprint_channels, collapse = "_"),
    ".rds"
  )
  
  train_cache_file <- paste0(
    "fingerprints_",
    train_gearbox,
    "_ch",
    paste(fingerprint_channels, collapse = "_"),
    ".rds"
  )
  
  # Check if test fingerprints exist, otherwise compute
  if (file.exists(test_cache_file)) {
    cat("Loading cached test fingerprints from:", test_cache_file, "\n")
    test_fingerprints_all <- readRDS(test_cache_file)
  } else {
    cat("Computing test fingerprints...\n")
    test_fingerprints_all <- precompute_spectral_fingerprints(
      test_gearbox_path,
      channels = fingerprint_channels,
      gearbox_name = basename(test_gearbox_path)
    )
    saveRDS(test_fingerprints_all, test_cache_file)
    cat("Saved test fingerprints to:", test_cache_file, "\n")
  }
  
  # Check if train fingerprints exist, otherwise compute
  if (file.exists(train_cache_file)) {
    cat("Loading cached train fingerprints from:", train_cache_file, "\n")
    train_fingerprints_all <- readRDS(train_cache_file)
  } else {
    cat("Computing train fingerprints...\n")
    train_fingerprints_all <- precompute_spectral_fingerprints(
      train_gearbox_path,
      channels = fingerprint_channels,
      gearbox_name = basename(train_gearbox_path)
    )
    saveRDS(train_fingerprints_all, train_cache_file)
    cat("Saved train fingerprints to:", train_cache_file, "\n")
  }

  # Extract test trajectory
  test_trajectory <- test_fingerprints_all[test_signal_indices, ]

  n_train <- nrow(train_fingerprints_all)
  window_size <- length(test_signal_indices)
  n_windows <- n_train - window_size + 1

  cat("Screening", n_windows, "windows...\n")

  similarities <- numeric(n_windows)

  for (i in 1:n_windows) {
    train_window <- train_fingerprints_all[i:(i + window_size - 1), ]
    similarities[i] <- compute_fingerprint_similarity(
      test_trajectory,
      train_window
    )

    if (i %% 200 == 0) {
      cat("  Screened", i, "of", n_windows, "windows\n")
    }
  }

  # Get top N candidates
  top_indices <- order(similarities, decreasing = TRUE)[1:top_n_candidates]

  candidates <- data.frame(
    Window_Start = top_indices,
    Window_End = top_indices + window_size - 1,
    Fingerprint_Similarity = similarities[top_indices]
  )

  cat("\nTop", top_n_candidates, "candidates selected\n")
  cat(
    "Similarity range:",
    round(min(candidates$Fingerprint_Similarity), 3),
    "to",
    round(max(candidates$Fingerprint_Similarity), 3),
    "\n\n"
  )

  return(list(
    candidates = candidates,
    test_fingerprints = test_fingerprints_all,
    train_fingerprints = train_fingerprints_all,
    full_feature_channels = full_feature_channels
  ))
}

# ============================================================================
# STAGE 2: FULL FEATURE EXTRACTION - MEMORY OPTIMIZED
# ============================================================================

precompute_all_features <- function(
  gearbox_path,
  channels = 1:11,
  preprocess = TRUE,
  gearbox_name = "Gearbox"
) {
  cat("=== Pre-computing features for", gearbox_name, "===\n")

  # Get number of signals by reading only first column
  channel_1_path <- file.path(gearbox_path, "channel_1.csv")
  n_signals <- nrow(fread(channel_1_path, select = 1L, header = TRUE))  # Only read first column to count rows

  cat("Total signals:", n_signals, "\n")
  cat("Channels:", length(channels), "\n")

  all_features_matrix <- NULL
  feature_names <- NULL

  for (signal_idx in 1:n_signals) {
    signal_features <- list()

    for (ch in channels) {
      channel_path <- file.path(gearbox_path, paste0("channel_", ch, ".csv"))
      
      # Read ONLY this one signal (one row) - MEMORY OPTIMIZED!
      signal <- fread(
        channel_path,
        skip = signal_idx - 1,
        nrows = 1,
        header = TRUE
      ) |> 
        unlist() |> 
        as.numeric()

      if (preprocess) {
        signal <- preprocess_signal(signal)
      }

      # Time-domain features
      td_features <- calculate_vibration_timeDomainFeatures(signal)

      # Frequency-domain features (spectral kurtosis summary)
      w_len <- 128
      o_len <- 0.8 * w_len

      spec_output <- specgram(
        signal,
        n = 512,
        Fs = 12800,
        overlap = o_len,
        window = hanning(w_len)
      )

      P_matrix <- Mod(spec_output$S)^2
      freq_bins <- spec_output$f

      # Exclude DC bin
      P_data <- P_matrix[-1, ]
      freq_data <- freq_bins[-1]

      # Calculate SK for frequency range >= 10 Hz (full range)
      freq_mask <- freq_data >= 10

      if (sum(freq_mask) > 0) {
        P_data_filtered <- P_data[freq_mask, ]

        num_freq_bins <- nrow(P_data_filtered)
        sk_values <- numeric(num_freq_bins)

        for (i in 1:num_freq_bins) {
          energy_envelope <- P_data_filtered[i, ]
          sk_values[i] <- e1071::kurtosis(energy_envelope, type = 1) + 1
        }

        sk_mean <- mean(sk_values, na.rm = TRUE)
        sk_max <- max(sk_values, na.rm = TRUE)
        sk_std <- sd(sk_values, na.rm = TRUE)
      } else {
        sk_mean <- NA
        sk_max <- NA
        sk_std <- NA
      }

      # Combine all features for this channel
      channel_features <- c(
        unlist(td_features),
        SK_Mean = sk_mean,
        SK_Max = sk_max,
        SK_Std = sk_std
      )

      # Add channel prefix to feature names
      names(channel_features) <- paste0("Ch", ch, ".", names(channel_features))
      signal_features[[ch]] <- channel_features
    }

    # Flatten features for this signal
    signal_feature_vector <- unlist(signal_features)

    # Initialize matrix on first signal
    if (is.null(all_features_matrix)) {
      n_features <- length(signal_feature_vector)
      all_features_matrix <- matrix(nrow = n_signals, ncol = n_features)
      feature_names <- names(signal_feature_vector)
      colnames(all_features_matrix) <- feature_names
    }

    all_features_matrix[signal_idx, ] <- signal_feature_vector

    # Progress every 10 signals
    if (signal_idx %% 10 == 0) {
      cat("  Processed signal", signal_idx, "of", n_signals, "\n")
    }
  }

  rownames(all_features_matrix) <- paste0("Signal_", 1:n_signals)

  cat("Feature extraction complete!\n")
  cat(
    "Matrix dimensions:",
    nrow(all_features_matrix),
    "signals x",
    ncol(all_features_matrix),
    "features\n\n"
  )

  return(all_features_matrix)
}

extract_trajectory_from_precomputed <- function(
  features_matrix,
  signal_indices
) {
  return(features_matrix[signal_indices, , drop = FALSE])
}

compare_trajectories <- function(trajectory1, trajectory2) {
  # Ensure same number of time points
  if (nrow(trajectory1) != nrow(trajectory2)) {
    stop("Trajectories must have the same number of time points")
  }

  if (ncol(trajectory1) != ncol(trajectory2)) {
    stop("Trajectories must have the same features")
  }

  n_timepoints <- nrow(trajectory1)
  n_features <- ncol(trajectory1)

  # Method 1: Correlation of feature trends
  correlations <- numeric(n_features)
  for (i in 1:n_features) {
    correlations[i] <- cor(
      trajectory1[, i],
      trajectory2[, i],
      use = "complete.obs"
    )
  }
  mean_correlation <- mean(correlations, na.rm = TRUE)

  # Method 2: Euclidean distance between normalized trajectories
  traj1_norm <- scale(trajectory1)
  traj2_norm <- scale(trajectory2)
  euclidean_dist <- sqrt(sum((traj1_norm - traj2_norm)^2, na.rm = TRUE))

  # Method 3: Cosine similarity of flattened trajectories
  vec1 <- as.vector(t(traj1_norm))
  vec2 <- as.vector(t(traj2_norm))
  valid_idx <- !is.na(vec1) & !is.na(vec2)
  cosine_sim <- sum(vec1[valid_idx] * vec2[valid_idx]) /
    (sqrt(sum(vec1[valid_idx]^2)) * sqrt(sum(vec2[valid_idx]^2)))

  return(list(
    mean_correlation = mean_correlation,
    euclidean_distance = euclidean_dist,
    cosine_similarity = cosine_sim
  ))
}

refine_candidates_with_full_features <- function(
  test_gearbox_path,
  train_gearbox_path,
  candidates,
  test_signal_indices = 1:5,
  test_features = NULL,
  train_features = NULL,
  channels = 1:11,
  preprocess = TRUE
) {
  cat("=== Stage 2: Full Feature Comparison on Top Candidates ===\n")

  # Pre-compute test features if not provided (only 5 signals)
  if (is.null(test_features)) {
    test_features <- precompute_all_features(
      test_gearbox_path,
      channels,
      preprocess,
      "Test"
    )
  }

  # For train features: extract only for candidate windows
  # Identify unique signal indices needed
  unique_train_signals <- unique(unlist(lapply(1:nrow(candidates), function(i) {
    candidates$Window_Start[i]:candidates$Window_End[i]
  })))
  unique_train_signals <- sort(unique_train_signals)
  
  cat("Need features for", length(unique_train_signals), "unique train signals (from 50 windows)\n")
  
  if (is.null(train_features)) {
    # Compute features ONLY for needed signals
    train_features_map <- list()
    
    for (sig_idx in unique_train_signals) {
      signal_features <- list()
      
      for (ch in channels) {
        channel_path <- file.path(train_gearbox_path, paste0("channel_", ch, ".csv"))
        
        signal <- fread(
          channel_path,
          skip = sig_idx - 1,
          nrows = 1,
          header = TRUE
        ) |> 
          unlist() |> 
          as.numeric()
        
        if (preprocess) {
          signal <- preprocess_signal(signal)
        }
        
        # Time-domain features
        td_features <- calculate_vibration_timeDomainFeatures(signal)
        
        # Frequency-domain features
        w_len <- 128
        o_len <- 0.8 * w_len
        
        spec_output <- specgram(
          signal,
          n = 512,
          Fs = 12800,
          overlap = o_len,
          window = hanning(w_len)
        )
        
        P_matrix <- Mod(spec_output$S)^2
        freq_bins <- spec_output$f
        P_data <- P_matrix[-1, ]
        freq_data <- freq_bins[-1]
        
        freq_mask <- freq_data >= 10
        
        if (sum(freq_mask) > 0) {
          P_data_filtered <- P_data[freq_mask, ]
          num_freq_bins <- nrow(P_data_filtered)
          sk_values <- numeric(num_freq_bins)
          
          for (i in 1:num_freq_bins) {
            energy_envelope <- P_data_filtered[i, ]
            sk_values[i] <- e1071::kurtosis(energy_envelope, type = 1) + 1
          }
          
          sk_mean <- mean(sk_values, na.rm = TRUE)
          sk_max <- max(sk_values, na.rm = TRUE)
          sk_std <- sd(sk_values, na.rm = TRUE)
        } else {
          sk_mean <- NA
          sk_max <- NA
          sk_std <- NA
        }
        
        channel_features <- c(
          unlist(td_features),
          SK_Mean = sk_mean,
          SK_Max = sk_max,
          SK_Std = sk_std
        )
        
        names(channel_features) <- paste0("Ch", ch, ".", names(channel_features))
        signal_features[[ch]] <- channel_features
      }
      
      train_features_map[[as.character(sig_idx)]] <- unlist(signal_features)
      
      if (which(unique_train_signals == sig_idx) %% 10 == 0) {
        cat("  Extracted features for", which(unique_train_signals == sig_idx), "of", length(unique_train_signals), "signals\n")
      }
    }
  }

  # Extract test trajectory
  test_trajectory <- extract_trajectory_from_precomputed(
    test_features,
    test_signal_indices
  )

  # Compare with candidates
  refined_results <- data.frame(
    Window_Start = integer(),
    Window_End = integer(),
    Fingerprint_Similarity = numeric(),
    Mean_Correlation = numeric(),
    Euclidean_Distance = numeric(),
    Cosine_Similarity = numeric()
  )

  for (i in 1:nrow(candidates)) {
    start_idx <- candidates$Window_Start[i]
    end_idx <- candidates$Window_End[i]
    window_indices <- start_idx:end_idx

    # Build train window from extracted features
    train_window <- matrix(nrow = length(window_indices), ncol = length(train_features_map[[1]]))
    for (j in seq_along(window_indices)) {
      train_window[j, ] <- train_features_map[[as.character(window_indices[j])]]
    }
    colnames(train_window) <- names(train_features_map[[1]])

    similarity <- compare_trajectories(test_trajectory, train_window)

    refined_results <- rbind(
      refined_results,
      data.frame(
        Window_Start = start_idx,
        Window_End = end_idx,
        Fingerprint_Similarity = candidates$Fingerprint_Similarity[i],
        Mean_Correlation = similarity$mean_correlation,
        Euclidean_Distance = similarity$euclidean_distance,
        Cosine_Similarity = similarity$cosine_similarity
      )
    )

    if (i %% 10 == 0) {
      cat("  Refined", i, "of", nrow(candidates), "candidates\n")
    }
  }

  # Compute composite score
  refined_results$Euclidean_Distance_Norm <- 1 -
    (refined_results$Euclidean_Distance - min(refined_results$Euclidean_Distance)) /
      (max(refined_results$Euclidean_Distance) - min(refined_results$Euclidean_Distance))

  refined_results$Composite_Score <- (
    refined_results$Mean_Correlation +
    refined_results$Cosine_Similarity +
    refined_results$Euclidean_Distance_Norm
  ) / 3

  refined_results <- refined_results |> arrange(desc(Composite_Score))

  cat("\n=== Refinement Complete ===\n")

  return(refined_results)
}

# ============================================================================
# COMPLETE PIPELINE
# ============================================================================

find_degradation_stage_fast_optimized <- function(
  test_gearbox = "G_6",
  test_set = "test_1",
  test_signal_indices = 1:5,
  train_gearbox = "G_1",
  base_path = "C:/Users/shish/Documents/rul_challenge_data",
  fingerprint_channels = c(4, 5, 9),  # Output shaft + acoustic for Stage 1
  full_feature_channels = 1:11,       # All channels for Stage 2
  top_n_candidates = 50,
  preprocess = TRUE,
  test_features = NULL,
  train_features = NULL
) {
  test_path <- file.path(base_path, "test", test_gearbox, test_set)
  train_path <- file.path(base_path, "train", train_gearbox)

  # Stage 1: Fast screening with GMF-based fingerprints
  stage1_output <- fast_candidate_selection_optimized(
    test_path,
    train_path,
    test_signal_indices,
    top_n_candidates,
    fingerprint_channels,
    full_feature_channels,
    test_gearbox = test_gearbox,    # Pass the value
    test_set = test_set,             # Pass the value
    train_gearbox = train_gearbox    # Pass the value
  )

  # Stage 2: Refined comparison with all channels
  final_results <- refine_candidates_with_full_features(
    test_path,
    train_path,
    stage1_output$candidates,
    test_signal_indices,
    test_features = test_features,
    train_features = train_features,
    channels = full_feature_channels,
    preprocess = preprocess
  )

  return(list(
    results = final_results,
    stage1_output = stage1_output
  ))
}

plot_degradation_matching <- function(results, train_gearbox = "G_1") {
  # Find best matches
  best_correlation <- results[which.max(results$Mean_Correlation), ]
  best_cosine <- results[which.max(results$Cosine_Similarity), ]
  best_euclidean <- results[which.min(results$Euclidean_Distance), ]
  best_composite <- results[which.max(results$Composite_Score), ]

  # Create interactive plot
  fig <- plot_ly(results, x = ~Window_Start) |>
    add_trace(
      y = ~Mean_Correlation,
      name = "Mean Correlation",
      type = 'scatter',
      mode = 'lines+markers',
      line = list(width = 2)
    ) |>
    add_trace(
      y = ~Cosine_Similarity,
      name = "Cosine Similarity",
      type = 'scatter',
      mode = 'lines+markers',
      line = list(width = 2)
    ) |>
    add_trace(
      y = ~Euclidean_Distance_Norm,
      name = "Euclidean (Normalized)",
      type = 'scatter',
      mode = 'lines+markers',
      line = list(width = 2)
    ) |>
    add_trace(
      y = ~Composite_Score,
      name = "Composite Score",
      type = 'scatter',
      mode = 'lines+markers',
      line = list(width = 2, dash = 'dash')
    ) |>
    layout(
      title = paste("G_6 Degradation Stage Matching with", train_gearbox),
      xaxis = list(title = paste(train_gearbox, "Signal Window Start Index")),
      yaxis = list(title = "Similarity Score", range = c(0, 1)),
      hovermode = "x unified"
    )

  # Print summary
  cat("\n=== Best Matches ===\n")
  cat(
    "By Mean Correlation:",
    best_correlation$Window_Start,
    "-",
    best_correlation$Window_End,
    "(score:",
    round(best_correlation$Mean_Correlation, 3),
    ")\n"
  )
  cat(
    "By Cosine Similarity:",
    best_cosine$Window_Start,
    "-",
    best_cosine$Window_End,
    "(score:",
    round(best_cosine$Cosine_Similarity, 3),
    ")\n"
  )
  cat(
    "By Euclidean Distance:",
    best_euclidean$Window_Start,
    "-",
    best_euclidean$Window_End,
    "(score:",
    round(best_euclidean$Euclidean_Distance, 2),
    ")\n"
  )
  cat(
    "By Composite Score:",
    best_composite$Window_Start,
    "-",
    best_composite$Window_End,
    "(score:",
    round(best_composite$Composite_Score, 3),
    ")\n"
  )

  return(fig)
}
```

Usage

```{r}
# Option 1: Let the function pre-compute features automatically
output_optimized <- find_degradation_stage_fast_optimized(
  test_gearbox = "G_6",
  test_set = "test_1",
  test_signal_indices = 1:5,
  train_gearbox = "G_1",
  fingerprint_channels = c(4, 5, 9),
  full_feature_channels = 1:11,
  top_n_candidates = 50,
  preprocess = TRUE
)

# View results
head(output_optimized$results, 10)

# Visualize
fig <- plot_degradation_matching(output_optimized$results, "G_1")
fig

# Save
saveRDS(output_optimized, "g6_test1_vs_g1_optimized_output.rds")
htmlwidgets::saveWidget(
  fig,
  "g6_test1_vs_g1_optimized_matching.html",
  selfcontained = TRUE
)
```

Using Cepstrum code from Gemini

```{r}
library(data.table)
library(dplyr)
library(signal)
library(e1071)
library(pracma)
library(plotly)

# ============================================================================
# HELPER 1: SHAFT SPEED FROM KEY PHASOR (Channel 7)
# ============================================================================
get_shaft_speed_from_keyphasor <- function(keyphasor_vec, Fs = 12800) {
  # 1. Normalize and Threshold
  # Key phasor is a pulse train. We find the rising edges.
  thresh <- (max(keyphasor_vec) - min(keyphasor_vec)) * 0.5 + min(keyphasor_vec)
  
  # 2. Find rising edges (0 -> 1 transitions)
  pulse_binary <- as.integer(keyphasor_vec > thresh)
  rising_edges <- which(diff(pulse_binary) == 1)
  
  if (length(rising_edges) < 2) return(list(hz = NA, edges = c()))
  
  # 3. Calculate average speed
  avg_samples_diff <- mean(diff(rising_edges))
  shaft_freq_hz <- Fs / avg_samples_diff
  
  return(list(hz = shaft_freq_hz, edges = rising_edges))
}

# ============================================================================
# HELPER 2: CEPSTRUM RAHMONIC AMPLITUDE (Stage 1 Feature)
# ============================================================================
compute_cepstrum_features <- function(signal_vec, Fs, input_shaft_hz) {
  n <- length(signal_vec)
  
  # 1. Gear Kinematics
  # Input: 2400 RPM (40 Hz). Pinion is on Intermediate Shaft.
  # Ratio: Input(29T) -> Intermediate(95T)
  intermediate_shaft_hz <- input_shaft_hz * (29/95) 
  
  # 2. Real Cepstrum
  spec <- Mod(fft(signal_vec))
  log_spec <- log(spec + 1e-10)
  cepstrum <- Re(fft(log_spec, inverse = TRUE) / n)
  
  # 3. Define Quefrency axis (seconds) & Half Cepstrum
  quefrency <- (0:(n/2 - 1)) / Fs
  cepstrum_half <- cepstrum[1:(n/2)]
  
  # 4. Target Quefrency: Period of the Intermediate Shaft (Fault Location)
  target_quefrency <- 1 / intermediate_shaft_hz
  
  # 5. Find Amplitude in search window (+/- 10 samples for jitter)
  target_idx <- which.min(abs(quefrency - target_quefrency))
  
  # Handle edge case if target_idx is too close to start
  start_win <- max(1, target_idx - 10)
  end_win <- min(length(cepstrum_half), target_idx + 10)
  
  rahmonic_amp <- max(cepstrum_half[start_win:end_win])
  
  return(rahmonic_amp)
}

# ============================================================================
# HELPER 3: TSA RESIDUAL FM4 (Stage 2 Feature)
# ============================================================================
compute_tsa_fm4 <- function(signal_vec, keyphasor_edges, Fs) {
  
  # We perform TSA synchronous to the Input Shaft (Key Phasor).
  # The fault is on the Intermediate Shaft (Non-synchronous).
  # Therefore, the fault will appear in the RESIDUAL signal.
  
  num_revs <- length(keyphasor_edges) - 1
  if (num_revs < 1) return(NA)
  
  # Target points per revolution for resampling
  target_points <- 2048 
  tsa_matrix <- matrix(0, nrow = num_revs, ncol = target_points)
  
  # 1. Angular Resampling
  for (i in 1:num_revs) {
    start_idx <- keyphasor_edges[i]
    end_idx <- keyphasor_edges[i+1]
    
    segment <- signal_vec[start_idx:end_idx]
    
    # Linear interpolation to stretch/shrink to fixed length
    tsa_matrix[i, ] <- approx(
      x = seq_along(segment), 
      y = segment, 
      n = target_points
    )$y
  }
  
  # 2. Compute TSA (Mean) and Residual (Difference)
  tsa_mean <- colMeans(tsa_matrix, na.rm = TRUE)
  residual_matrix <- sweep(tsa_matrix, 2, tsa_mean, "-")
  
  # 3. FM4 (Kurtosis) of the Residual
  # Flatten the matrix to treat it as one continuous residual signal
  residual_signal <- as.vector(residual_matrix)
  fm4 <- kurtosis(residual_signal)
  
  return(fm4)
}

# ============================================================================
# MAIN PROCESSING FUNCTION (Handles Row-wise Structure)
# ============================================================================
process_gearbox_data <- function(
  folder_path,
  vib_channels = c(4, 5), 
  keyphasor_channel = 7,
  indices_to_process = NULL # If NULL, process all rows
) {
  
  cat(paste("Loading data from:", basename(folder_path), "\n"))
  
  # 1. Load the Key Phasor File (Channel 7)
  # We assume the file name format is "channel_7.csv"
  kp_path <- file.path(folder_path, paste0("channel_", keyphasor_channel, ".csv"))
  if (!file.exists(kp_path)) stop("Key Phasor file not found: ", kp_path)
  
  # Read entire file (faster than row-by-row)
  # data.table::fread is very efficient for this size (~150MB)
  dt_kp <- fread(kp_path, header = TRUE) 
  
  # Determine which rows to process
  if (is.null(indices_to_process)) {
    rows_to_run <- 1:nrow(dt_kp)
  } else {
    rows_to_run <- indices_to_process
  }
  
  # 2. Load Vibration Channels
  vib_data_list <- list()
  for (ch in vib_channels) {
    vib_path <- file.path(folder_path, paste0("channel_", ch, ".csv"))
    cat(paste("  Loading Channel", ch, "...\n"))
    vib_data_list[[as.character(ch)]] <- fread(vib_path, header = TRUE)
  }
  
  # 3. Process Rows
  cat("  Computing features...\n")
  results_list <- list()
  
  # We iterate through the requested row indices
  # Note: i is the actual row index in the CSV
  for (i in rows_to_run) {
    
    # Extract row as numeric vector
    # unlist ensures we get a vector, not a 1-row data.table
    kp_vec <- as.numeric(dt_kp[i, ])
    
    # Get Speed Info
    kp_info <- get_shaft_speed_from_keyphasor(kp_vec)
    
    if (is.na(kp_info$hz)) {
      # Handle cases where engine might be off or sensor bad
      next 
    }
    
    # Initialize result row
    row_res <- list(Row_Index = i, Input_RPM = kp_info$hz * 60)
    
    # Compute features for each vibration channel
    for (ch in vib_channels) {
      # Extract vibration signal vector for this row
      sig_vec <- as.numeric(vib_data_list[[as.character(ch)]][i, ])
      
      # Stage 1: Cepstrum
      cep_amp <- compute_cepstrum_features(sig_vec, Fs = 12800, kp_info$hz)
      row_res[[paste0("Cepstrum_Ch", ch)]] <- cep_amp
      
      # Stage 2: TSA FM4
      fm4_val <- compute_tsa_fm4(sig_vec, kp_info$edges, Fs = 12800)
      row_res[[paste0("FM4_Ch", ch)]] <- fm4_val
    }
    
    results_list[[length(results_list) + 1]] <- as.data.frame(row_res)
    
    if (length(results_list) %% 100 == 0) cat(paste("    Processed", length(results_list), "signals\n"))
  }
  
  return(bind_rows(results_list))
}

# # ============================================================================
# MODIFIED MATCHING LOGIC (Returns Top N Matches)
# ============================================================================
find_matching_sequence <- function(test_df, train_df, top_n = 25) {
  # We are matching 5 rows of Test against N rows of Train
  window_size <- nrow(test_df)
  
  # Extract Cepstrum columns only for matching
  cols_to_use <- grep("Cepstrum", names(test_df), value = TRUE)
  
  test_vec <- as.vector(as.matrix(test_df[, cols_to_use]))
  # Normalize test vector once
  test_norm <- sqrt(sum(test_vec^2))
  
  n_train <- nrow(train_df)
  n_windows <- n_train - window_size + 1
  similarities <- numeric(n_windows)
  
  for (i in 1:n_windows) {
    # Extract window from training data
    window_data <- train_df[i:(i + window_size - 1), cols_to_use]
    train_vec <- as.vector(as.matrix(window_data))
    
    train_norm <- sqrt(sum(train_vec^2))
    
    # Cosine Similarity
    if (train_norm == 0 || test_norm == 0) {
      similarities[i] <- 0
    } else {
      similarities[i] <- sum(test_vec * train_vec) / (test_norm * train_norm)
    }
  }
  
  # --- NEW LOGIC: Extract Top N Matches ---
  # Get indices of the top N scores
  top_indices <- order(similarities, decreasing = TRUE)[1:min(top_n, length(similarities))]
  
  # Create a summary dataframe for the top matches
  # We map the window index 'i' back to the actual 'Row_Index' from the training dataframe
  top_matches_df <- data.frame(
    Rank = 1:length(top_indices),
    Start_Index_G1 = train_df$Row_Index[top_indices],
    Similarity = similarities[top_indices]
  )
  
  return(list(
    best_match = top_matches_df[1, ],      # The #1 result
    top_matches = top_matches_df,          # Table of top N results
    all_scores = similarities              # For plotting the full curve
  ))
}

```


```{r}


# ============================================================================
# EXECUTION BLOCK
# ============================================================================

# 1. Configuration
base_path <- "C:/Users/shish/Documents/rul_challenge_data"
train_folder <- file.path(base_path, "train", "G_1")
test_folder  <- file.path(base_path, "test", "G_6", "test_5")

# # 2. Process Training Data (G_1) - Full Lifecycle
# # This loads all rows from channel_4.csv, channel_5.csv, channel_7.csv
# train_features <- process_gearbox_data(
#   folder_path = train_folder,
#   vib_channels = c(4, 5),
#   keyphasor_channel = 7
# )

# 3. Process Test Data (G_6) - Specific 5 rows
# Assuming the 5 files in "test_1" correspond to rows 1 to 5 in the channel CSVs
test_features <- process_gearbox_data(
  folder_path = test_folder,
  vib_channels = c(4, 5),
  keyphasor_channel = 7,
  indices_to_process = 1:5
)

# ============================================================================
# STEP 4: FIND THE MATCHES
# ============================================================================
# Configure how many top matches you want to analyze
TOP_N_COUNT <- 25 

match_result <- find_matching_sequence(
  test_features, 
  train_features, 
  top_n = TOP_N_COUNT
)

# ============================================================================
# STEP 5: REPORT RESULTS & CLUSTERING METRICS
# ============================================================================
best_match <- match_result$best_match
top_matches <- match_result$top_matches

cat("\n=== MATCHING RESULTS ===\n")
cat(sprintf("Best match starts at G1 Signal Row: %d\n", best_match$Start_Index_G1))
cat(sprintf("Cosine Similarity Score:            %.4f\n", best_match$Similarity))

life_percentage <- (best_match$Start_Index_G1 / nrow(train_features)) * 100
cat(sprintf("Estimated Degradation Stage:        %.1f%% of useful life\n", life_percentage))

# --- CLUSTERING ANALYSIS ---
# Calculate the spread (Standard Deviation) of the top N locations
spread_sd <- sd(top_matches$Start_Index_G1)
spread_range <- max(top_matches$Start_Index_G1) - min(top_matches$Start_Index_G1)

cat(sprintf("\n=== CONFIDENCE METRICS (Top %d) ===\n", TOP_N_COUNT))
cat(sprintf("Spread (Standard Deviation):        %.2f indices\n", spread_sd))
cat(sprintf("Full Range (Max - Min index):       %d indices\n", spread_range))

if (spread_sd < 50) {
  cat("VERDICT: High Confidence (Matches are tightly clustered)\n")
} else if (spread_sd < 150) {
  cat("VERDICT: Medium Confidence (Some spread in matches)\n")
} else {
  cat("VERDICT: Low Confidence (Matches are widely scattered)\n")
}

# ============================================================================
# STEP 6: VISUALIZATION WITH TOP MATCHES
# ============================================================================
plot_data <- data.frame(
  Index = 1:length(match_result$all_scores),
  Similarity = match_result$all_scores
)

# Base Line Plot
fig <- plot_ly(plot_data, x = ~Index, y = ~Similarity) %>%
  add_lines(name = "Similarity Curve", line = list(color = 'rgb(31, 119, 180)')) %>%
  
  # Add Red Dots for Top N Matches
  add_trace(
    data = top_matches,
    x = ~Start_Index_G1,
    y = ~Similarity,
    type = 'scatter',
    mode = 'markers',
    name = paste('Top', TOP_N_COUNT, 'Matches'),
    marker = list(color = 'red', size = 8, symbol = 'circle-open'),
    text = ~paste("Rank:", Rank, "<br>Score:", round(Similarity, 4))
  ) %>%
  
  layout(
    title = paste("Matching G6 Signals (1-5) against G1 Lifecycle (Cepstrum)"),
    xaxis = list(title = "G1 Signal Index (Time)"),
    yaxis = list(title = "Cosine Similarity"),
    legend = list(x = 0.8, y = 0.9)
  )

fig
```


First, I need the pre processing functions defined in your environment. 

```{r}

preprocess_signal <- function(signal_vector, Fs = 12800) {
  # Step 1: Detrending - Remove the mean
  detrended_signal <- signal_vector - mean(signal_vector)

  # Step 2: Low-pass filtering
  # Calculate Nyquist frequency
  nyquist_freq <- Fs / 2

  # Set cutoff frequency at 90% of Nyquist
  cutoff_freq <- 1 * nyquist_freq

  # Normalize cutoff frequency (between 0 and 1, where 1 is Nyquist)
  W <- cutoff_freq / nyquist_freq

  # Design Butterworth filter (4th order)
  butter_filter <- butter(n = 4, W = W, type = "low")

  # Apply the filter
  filtered_signal <- filtfilt(butter_filter, detrended_signal)

  return(filtered_signal)
}


calculate_vibration_timeDomainFeatures <- function(signal_vector) {
  # --- Intermediate Calculations ---
  abs_signal <- abs(signal_vector)

  # Peak Value (Maximum Absolute Amplitude, xp)
  peak_value <- max(abs_signal)

  # RMS: Root Mean Square
  rms_value <- sqrt(mean(signal_vector^2))

  # Absolute Mean (Mean of the absolute values, or Rectified Mean)
  abs_mean <- mean(abs_signal)

  # Denominator for Margin Factor
  # Formula: ( 1/N * sum(|x_i|) )^2
  margin_denominator <- (abs_mean)^2

  # --- Feature Calculations ---
  results <- list(
    # Basic Stats
    Mean = mean(signal_vector),
    Std_Dev = sd(signal_vector),
    Peak_to_Peak = max(signal_vector) - min(signal_vector),
    RMS = rms_value,

    # Statistical Moments
    Skewness = skewness(signal_vector),
    Kurtosis = kurtosis(signal_vector),

    # Factors (using the robust peak_value = max(|x|))
    Crest_Factor = peak_value / rms_value,
    Shape_Factor = rms_value / abs_mean,
    Impulse_Factor = peak_value / abs_mean,

    # Margin Factor (Denominator: Squared Mean of the Absolute Values)
    Margin_Factor = peak_value / margin_denominator,

    # Energy
    Energy = sum(signal_vector^2) # Sum of Squares
  )

  return(results)
}


process_channel_features <- function(channel_data, Fs = 12800) {
  # Initialize output lists
  time_domain_features_list <- list()
  sk_summary_features_list <- list()

  # Get number of signals (rows)
  n_signals <- nrow(channel_data)

  # Process each signal
  for (row_idx in 1:n_signals) {
    # --- 1. Extract and preprocess signal ---
    signal_vector <- channel_data[row_idx, ] |> unlist() |> as.numeric()

    # Preprocess: detrend and filter
    signal_vector <- preprocess_signal(signal_vector, Fs = Fs)

    # --- 2. Calculate Time Domain Features ---
    time_features <- calculate_vibration_timeDomainFeatures(signal_vector)
    time_domain_features_list[[row_idx]] <- as.data.frame(time_features)

    # --- 3. Calculate Spectral Kurtosis (Window length 32 only) ---
    w_len <- 32
    o_len <- 0.8 * w_len

    # Compute spectrogram
    spec_output <- specgram(
      signal_vector,
      n = 1024,
      Fs = Fs,
      overlap = o_len,
      window = hanning(w_len)
    )

    P_matrix <- Mod(spec_output$S)^2
    freq_bins <- spec_output$f

    # Exclude DC bin
    P_data <- P_matrix[-1, ]
    freq_data <- freq_bins[-1]

    # Calculate SK for each frequency bin
    num_freq_bins <- nrow(P_data)
    sk_values <- numeric(num_freq_bins)

    for (i in 1:num_freq_bins) {
      energy_envelope <- P_data[i, ]
      sk_values[i] <- e1071::kurtosis(energy_envelope, type = 1) + 1
    }

    # --- 4. Calculate SK Summary Features (> 10 Hz) ---
    # Filter for frequency range
    freq_mask <- freq_data >= 10 # & freq_data <= 5500
    sk_vals <- sk_values[freq_mask]
    freq_vals <- freq_data[freq_mask]

    # Calculate area under curve using trapezoidal rule
    average_heights <- (sk_vals[-length(sk_vals)] + sk_vals[-1]) / 2
    widths <- diff(freq_vals)
    area_under_curve <- sum(average_heights * widths)

    # Calculate summary statistics
    sk_summary_df <- data.frame(
      Window_Size = w_len,
      Mean_SK = mean(sk_vals, na.rm = TRUE),
      StdDev_SK = sd(sk_vals, na.rm = TRUE),
      Kurtosis_SK = e1071::kurtosis(sk_vals),
      Skewness_SK = e1071::skewness(sk_vals),
      PeakToPeak_SK = max(sk_vals, na.rm = TRUE) - min(sk_vals, na.rm = TRUE),
      AUC_SK = area_under_curve
    )

    sk_summary_features_list[[row_idx]] <- sk_summary_df

    # Progress indicator
    if (row_idx %% 100 == 0) {
      cat("Processed signal", row_idx, "of", n_signals, "\n")
    }
  }

  # Return only the two lists
  return(list(
    time_domain_features = time_domain_features_list,
    sk_summary_features = sk_summary_features_list
  ))
}
```

We will only look at the gear mesh frequencies and their harmonics.

```{r}
extract_spectral_fingerprint <- function(
  signal,
  Fs = 12800,
  preprocess = TRUE,
  freq_min = 10,
  freq_max = 6400,
  gearbox_group = "G_1_to_G_3"
) {
  if (preprocess) {
    signal <- preprocess_signal(signal)
  }

  # Compute FFT
  n <- length(signal)
  fft_result <- fft(signal)
  magnitude <- Mod(fft_result[1:(n / 2)])
  freqs <- (0:(n / 2 - 1)) * Fs / n

  # Use full frequency range
  freq_mask <- freqs >= freq_min & freqs <= freq_max
  magnitude_filtered <- magnitude[freq_mask]
  freqs_filtered <- freqs[freq_mask]

  # Define gear mesh frequencies based on gearbox group
  GMF1 <- 1160      # Test gearbox: Input-Intermediate mesh
  GMF2 <- 439.6     # Test gearbox: Intermediate-Output mesh (PINION)
  
  # Extract energy at GMF harmonics (THIS IS STANDARD)
  extract_gmf_harmonics <- function(gmf, n_harmonics = 5, bandwidth = 20) {
    harmonic_energies <- numeric(n_harmonics)
    for (h in 1:n_harmonics) {
      freq_center <- gmf * h
      # Find energy in narrow band around harmonic
      freq_range <- (freqs_filtered >= (freq_center - bandwidth)) & 
                    (freqs_filtered <= (freq_center + bandwidth))
      if (sum(freq_range) > 0) {
        harmonic_energies[h] <- sum(magnitude_filtered[freq_range]^2)
      } else {
        harmonic_energies[h] <- 0
      }
    }
    return(harmonic_energies)
  }
  
  # Extract GMF harmonics (physically meaningful)
  gmf1_harmonics <- extract_gmf_harmonics(GMF1, n_harmonics = 3)
  gmf2_harmonics <- extract_gmf_harmonics(GMF2, n_harmonics = 5)  # More important

  # Standard spectral features
  total_energy <- sum(magnitude_filtered^2)
  
  spectral_centroid <- sum(freqs_filtered * magnitude_filtered) /
    sum(magnitude_filtered)

  spectral_spread <- sqrt(
    sum(((freqs_filtered - spectral_centroid)^2) * magnitude_filtered) /
      sum(magnitude_filtered)
  )

  cumsum_energy <- cumsum(magnitude_filtered^2)
  rolloff_idx <- which(cumsum_energy >= 0.85 * total_energy)[1]
  spectral_rolloff <- freqs_filtered[rolloff_idx]

  rms <- sqrt(mean(signal^2))
  
  # High frequency energy ratio (standard for impact detection)
  high_freq_mask <- freqs_filtered >= 3000
  high_freq_energy_ratio <- sum(magnitude_filtered[high_freq_mask]^2) / total_energy

  return(c(
    Spectral_Centroid = spectral_centroid,
    Spectral_Spread = spectral_spread,
    Spectral_Rolloff = spectral_rolloff,
    RMS = rms,
    High_Freq_Energy_Ratio = high_freq_energy_ratio,
    # GMF2 features (pinion mesh - MOST IMPORTANT for your failure mode)
    GMF2_H1 = gmf2_harmonics[1],
    GMF2_H2 = gmf2_harmonics[2],
    GMF2_H3 = gmf2_harmonics[3],
    GMF2_H4 = gmf2_harmonics[4],
    GMF2_H5 = gmf2_harmonics[5],
    # GMF1 features (for context)
    GMF1_H1 = gmf1_harmonics[1],
    GMF1_H2 = gmf1_harmonics[2],
    GMF1_H3 = gmf1_harmonics[3]
  ))
}

# Modified fingerprint computation with gearbox group awareness
precompute_spectral_fingerprints <- function(
  gearbox_path,
  channels = c(4, 5, 9),  # Focus on output shaft + acoustic
  gearbox_name = "Gearbox",
  gearbox_group = NULL  # Automatically detect from path
) {
  cat("=== Computing spectral fingerprints for", gearbox_name, "===\n")
  
  # Auto-detect gearbox group if not provided
  if (is.null(gearbox_group)) {
    if (grepl("G_[123]", gearbox_path)) {
      gearbox_group <- "G_1_to_G_3"
    } else if (grepl("G_[456]", gearbox_path)) {
      gearbox_group <- "G_4_to_G_6"
    } else {
      warning("Could not detect gearbox group, defaulting to G_1_to_G_3")
      gearbox_group <- "G_1_to_G_3"
    }
  }
  
  cat("Detected gearbox group:", gearbox_group, "\n")

  channel_1_data <- fread(
    file.path(gearbox_path, paste0("channel_", channels[1], ".csv")),
    header = TRUE
  )
  n_signals <- nrow(channel_1_data)

  fingerprints_matrix <- matrix(nrow = n_signals, ncol = 18)  # Updated: 18 features now
  colnames(fingerprints_matrix) <- c(
    "Spectral_Centroid",
    "Top_Freq_1", "Top_Freq_2", "Top_Freq_3", "Top_Freq_4", "Top_Freq_5",
    "Spectral_Spread", "Spectral_Rolloff", "RMS", "High_Freq_Energy_Ratio",
    "GMF2_H1", "GMF2_H2", "GMF2_H3", "GMF2_H4", "GMF2_H5",
    "GMF1_H1", "GMF1_H2", "GMF1_H3"
  )

  for (signal_idx in 1:n_signals) {
    # Average fingerprint across selected channels
    channel_fingerprints <- matrix(nrow = length(channels), ncol = 18)

    for (i in seq_along(channels)) {
      ch <- channels[i]
      channel_data <- fread(
        file.path(gearbox_path, paste0("channel_", ch, ".csv")),
        header = TRUE
      )
      signal <- channel_data[signal_idx, ] |> unlist() |> as.numeric()
      channel_fingerprints[i, ] <- extract_spectral_fingerprint(
        signal,
        gearbox_group = gearbox_group
      )
    }

    # Average across channels
    fingerprints_matrix[signal_idx, ] <- colMeans(
      channel_fingerprints,
      na.rm = TRUE
    )

    if (signal_idx %% 100 == 0) {
      cat("  Processed", signal_idx, "of", n_signals, "\n")
    }
  }

  rownames(fingerprints_matrix) <- paste0("Signal_", 1:n_signals)
  cat("Fingerprint extraction complete!\n\n")

  return(fingerprints_matrix)
}

# Updated candidate selection
fast_candidate_selection_optimized <- function(
  test_gearbox_path,
  train_gearbox_path,
  test_signal_indices = 1:5,
  top_n_candidates = 50,
  fingerprint_channels = c(4, 5, 9),  # Output shaft + acoustic
  full_feature_channels = 1:11
) {
  cat("=== Stage 1: Fast Spectral Fingerprint Screening ===\n")
  cat("Using channels:", paste(fingerprint_channels, collapse = ", "), 
      "(Output shaft vibrations + Acoustic emission)\n")
  cat("Focusing on pinion failure signatures (GMF2 harmonics)\n\n")

  # Compute fingerprints - will auto-detect gearbox group
  test_fingerprints_all <- precompute_spectral_fingerprints(
    test_gearbox_path,
    channels = fingerprint_channels,
    gearbox_name = basename(test_gearbox_path)
  )
  train_fingerprints_all <- precompute_spectral_fingerprints(
    train_gearbox_path,
    channels = fingerprint_channels,
    gearbox_name = basename(train_gearbox_path)
  )

  # Extract test trajectory
  test_trajectory <- test_fingerprints_all[test_signal_indices, ]

  n_train <- nrow(train_fingerprints_all)
  window_size <- length(test_signal_indices)
  n_windows <- n_train - window_size + 1

  cat("Screening", n_windows, "windows...\n")

  similarities <- numeric(n_windows)

  for (i in 1:n_windows) {
    train_window <- train_fingerprints_all[i:(i + window_size - 1), ]
    similarities[i] <- compute_fingerprint_similarity(
      test_trajectory,
      train_window
    )

    if (i %% 200 == 0) {
      cat("  Screened", i, "of", n_windows, "windows\n")
    }
  }

  # Get top N candidates
  top_indices <- order(similarities, decreasing = TRUE)[1:top_n_candidates]

  candidates <- data.frame(
    Window_Start = top_indices,
    Window_End = top_indices + window_size - 1,
    Fingerprint_Similarity = similarities[top_indices]
  )

  cat("\nTop", top_n_candidates, "candidates selected\n")
  cat(
    "Similarity range:",
    round(min(candidates$Fingerprint_Similarity), 3),
    "to",
    round(max(candidates$Fingerprint_Similarity), 3),
    "\n\n"
  )

  return(list(
    candidates = candidates,
    test_fingerprints = test_fingerprints_all,
    train_fingerprints = train_fingerprints_all,
    full_feature_channels = full_feature_channels
  ))
}

# Updated pipeline
find_degradation_stage_fast_optimized <- function(
  test_gearbox = "G_6",
  test_set = "test_1",
  test_signal_indices = 1:5,
  train_gearbox = "G_1",
  base_path = "C:/Users/shish/Documents/rul_challenge_data",
  fingerprint_channels = c(4, 5, 9),  # Output shaft + acoustic
  full_feature_channels = 1:11,
  top
```


ROUGH

Here is the function that plots the three graphs: Power (dB) vs Frequency, Power (RMS) vs Frequency and Spectral Kurtosis vs Frequency for different window sizes.

Note that we have used L2 normalization for Power (RMS) and Spectral Kurtosis. You can disable it by setting l2_normalize = FALSE while calling the function.

```{r}
create_psd_comparison_viewer <- function(
  channel_data,
  channel_name = "Channel",
  Fs = 12800,
  window_lengths = c(32, 64, 128, 256),
  signal_step = 30,
  preprocess = TRUE,
  l2_normalize = TRUE
) {
  # Determine which signals to process (every 30th)
  row_indices_to_process <- seq(
    from = 1,
    to = nrow(channel_data),
    by = signal_step
  )

  if (length(row_indices_to_process) == 0) {
    stop("Input 'channel_data' is empty or has zero rows.")
  }

  n_signals_count <- length(row_indices_to_process)
  cat(
    "Processing",
    n_signals_count,
    "signals (every",
    signal_step,
    "rows) for",
    channel_name,
    "\n"
  )

  all_data <- data.frame()

  # Process each signal
  for (idx in row_indices_to_process) {
    signal_vector <- channel_data[idx, ] |> unlist() |> as.numeric()

    # Preprocess if requested
    if (preprocess) {
      signal_vector <- preprocess_signal(signal_vector, Fs = Fs)
    }

    # Calculate PSD and SK for each window length
    for (w_len in window_lengths) {
      o_len <- 0.8 * w_len

      # Compute spectrogram
      spec_output <- specgram(
        signal_vector,
        n = 512,
        Fs = Fs,
        overlap = o_len,
        window = hanning(w_len)
      )

      # Calculate power spectral density (average power across time)
      P_matrix <- Mod(spec_output$S)^2
      freq_bins <- spec_output$f

      # Exclude DC bin
      P_data <- P_matrix[-1, ]
      freq_data <- freq_bins[-1]

      # Average power across time for each frequency
      avg_power <- rowMeans(P_data)

      # Convert to dB scale
      power_db <- 10 * log10(avg_power + 1e-12)

      # Calculate RMS (square root of power)
      power_rms <- sqrt(avg_power)

      # Calculate Spectral Kurtosis for each frequency bin
      num_freq_bins <- nrow(P_data)
      sk_values <- numeric(num_freq_bins)

      for (i in 1:num_freq_bins) {
        energy_envelope <- P_data[i, ]
        sk_values[i] <- e1071::kurtosis(energy_envelope, type = 1) + 1
      }

      # Apply L2 normalization if requested
      if (l2_normalize) {
        # L2 norm for Power RMS
        l2_norm_rms <- sqrt(sum(power_rms^2))
        power_rms_normalized <- power_rms / l2_norm_rms

        # L2 norm for Spectral Kurtosis
        l2_norm_sk <- sqrt(sum(sk_values^2))
        sk_normalized <- sk_values / l2_norm_sk

        signal_data <- data.frame(
          Signal = idx,
          Frequency_kHz = freq_data / 1000,
          Power_dB = power_db,
          Power_RMS = power_rms_normalized,
          Spectral_Kurtosis = sk_normalized,
          Window_Size = as.factor(w_len)
        )
      } else {
        signal_data <- data.frame(
          Signal = idx,
          Frequency_kHz = freq_data / 1000,
          Power_dB = power_db,
          Power_RMS = power_rms,
          Spectral_Kurtosis = sk_values,
          Window_Size = as.factor(w_len)
        )
      }

      all_data <- rbind(all_data, signal_data)
    }

    if (which(row_indices_to_process == idx) %% 10 == 0) {
      cat(
        "Processed",
        which(row_indices_to_process == idx),
        "of",
        n_signals_count,
        "signals\n"
      )
    }
  }

  if (nrow(all_data) == 0) {
    warning("No data generated for plotting. Returning NULL.")
    return(NULL)
  }

  # Convert Signal to factor with proper ordering
  signal_levels <- as.character(unique(all_data$Signal))
  all_data$Signal <- factor(all_data$Signal, levels = signal_levels)

  # Determine y-axis label suffix
  norm_suffix <- if (l2_normalize) " (L2 Normalized)" else ""

  # Create first plot - Power in dB
  fig_db <- plot_ly(
    all_data,
    x = ~Frequency_kHz,
    y = ~Power_dB,
    color = ~Window_Size,
    frame = ~Signal,
    type = 'scatter',
    mode = 'lines',
    line = list(width = 2)
  ) |>
    layout(
      title = paste("Power Spectral Density (dB) -", channel_name),
      xaxis = list(
        title = "Frequency [kHz]",
        range = c(0, Fs / 2000)
      ),
      yaxis = list(
        title = "Power [dB]"
      )
    ) |>
    animation_opts(
      frame = 500,
      transition = 300,
      redraw = TRUE
    ) |>
    animation_slider(
      currentvalue = list(
        prefix = "Signal Index: ",
        visible = TRUE
      )
    ) |>
    animation_button(
      x = 0.1,
      y = 1.1
    )

  # Create second plot - Power RMS
  fig_rms <- plot_ly(
    all_data,
    x = ~Frequency_kHz,
    y = ~Power_RMS,
    color = ~Window_Size,
    frame = ~Signal,
    type = 'scatter',
    mode = 'lines',
    line = list(width = 2)
  ) |>
    layout(
      title = paste("Power Spectral Density (RMS) -", channel_name),
      xaxis = list(
        title = "Frequency [kHz]",
        range = c(0, Fs / 2000)
      ),
      yaxis = list(
        title = paste0("Power [RMS]", norm_suffix)
      )
    ) |>
    animation_opts(
      frame = 500,
      transition = 300,
      redraw = TRUE
    ) |>
    animation_slider(
      currentvalue = list(
        prefix = "Signal Index: ",
        visible = TRUE
      )
    ) |>
    animation_button(
      x = 0.1,
      y = 1.1
    )

  # Create third plot - Spectral Kurtosis
  fig_sk <- plot_ly(
    all_data,
    x = ~Frequency_kHz,
    y = ~Spectral_Kurtosis,
    color = ~Window_Size,
    frame = ~Signal,
    type = 'scatter',
    mode = 'lines',
    line = list(width = 2)
  ) |>
    layout(
      title = paste("Spectral Kurtosis -", channel_name),
      xaxis = list(
        title = "Frequency [kHz]",
        range = c(0, Fs / 2000)
      ),
      yaxis = list(
        title = paste0("Spectral Kurtosis", norm_suffix)
      )
    ) |>
    animation_opts(
      frame = 500,
      transition = 300,
      redraw = TRUE
    ) |>
    animation_slider(
      currentvalue = list(
        prefix = "Signal Index: ",
        visible = TRUE
      )
    ) |>
    animation_button(
      x = 0.1,
      y = 1.1
    )

  # Return all three plots as a list
  return(list(
    fig_db = fig_db,
    fig_rms = fig_rms,
    fig_sk = fig_sk
  ))
}
```

Example


```{r}
# Load a channel
channel_data <- fread(
  "C:/Users/shish/Documents/rul_challenge_data/train/G_4/channel_5.csv",
  header = TRUE
)

channel_data <- fread(
  "C:/Users/shish/Documents/rul_challenge_data/test/G_6/test_2/channel_5.csv",
  header = TRUE
)

# With L2 normalization (default)
plots <- create_psd_comparison_viewer(
  channel_data = channel_data,
  channel_name = "G_4 Channel 5",
  window_lengths = c(32, 64, 128, 256, 512),
  signal_step = 30,
  preprocess = TRUE,
  l2_normalize = TRUE
)

# Display all three plots
plots$fig_db
plots$fig_rms
plots$fig_sk
```

Next, I want a function that computes the cosine similarity between two signals. I want the cosine similarity computed based on 3 different metrics: Power (dB), Power (RMS) and Spectral Kurtosis. The function should take in two signals and output a data frame with the cosine similarity values for the three metrics.


```{r}
compute_cosine_similarity <- function(
  signal1,
  signal2,
  Fs = 12800,
  window_length = 128,
  overlap_fraction = 0.8,
  preprocess = TRUE
) {
  # Preprocess signals if requested
  if (preprocess) {
    signal1 <- preprocess_signal(signal1, Fs = Fs)
    signal2 <- preprocess_signal(signal2, Fs = Fs)
  }

  o_len <- overlap_fraction * window_length

  # Function to compute PSD and SK for a signal
  compute_metrics <- function(signal_vector) {
    spec_output <- specgram(
      signal_vector,
      n = 512,
      Fs = Fs,
      overlap = o_len,
      window = hanning(window_length)
    )

    P_matrix <- Mod(spec_output$S)^2
    freq_bins <- spec_output$f

    # Exclude DC bin
    P_data <- P_matrix[-1, ]
    freq_data <- freq_bins[-1]

    # Average power across time for each frequency
    avg_power <- rowMeans(P_data)

    # Convert to dB scale
    power_db <- 10 * log10(avg_power + 1e-12)

    # Calculate RMS (square root of power)
    power_rms <- sqrt(avg_power)

    # Calculate Spectral Kurtosis for each frequency bin
    num_freq_bins <- nrow(P_data)
    sk_values <- numeric(num_freq_bins)

    for (i in 1:num_freq_bins) {
      energy_envelope <- P_data[i, ]
      sk_values[i] <- e1071::kurtosis(energy_envelope, type = 1) + 1
    }

    return(list(
      Power_dB = power_db,
      Power_RMS = power_rms,
      Spectral_Kurtosis = sk_values
    ))
  }

  # Compute metrics for both signals
  metrics1 <- compute_metrics(signal1)
  metrics2 <- compute_metrics(signal2)

  # Function to compute cosine similarity
  cosine_similarity <- function(vec1, vec2) {
    sum(vec1 * vec2) / (sqrt(sum(vec1^2)) * sqrt(sum(vec2^2)))
  }

  # Calculate cosine similarities
  cos_sim_db <- cosine_similarity(metrics1$Power_dB, metrics2$Power_dB)
  cos_sim_rms <- cosine_similarity(metrics1$Power_RMS, metrics2$Power_RMS)
  cos_sim_sk <- cosine_similarity(
    metrics1$Spectral_Kurtosis,
    metrics2$Spectral_Kurtosis
  )
  # Create output data frame
  result_df <- data.frame(
    Metric = c("Power_dB", "Power_RMS", "Spectral_Kurtosis"),
    Cosine_Similarity = c(cos_sim_db, cos_sim_rms, cos_sim_sk)
  )
  return(result_df)
}
```

Usage example:

```{r}
# Load two signals, one from G_1 channel 5 and another from G_2 channel 5. Use fread to extract a single row as numeric vectors.

channel1_data <- fread(
  "C:/Users/shish/Documents/rul_challenge_data/train/G_1/channel_5.csv",
  header = TRUE,
  skip = 24,
  nrows = 1
) |>
  unlist() |>
  as.numeric()

channel2_data <- fread(
  "C:/Users/shish/Documents/rul_challenge_data/train/G_2/channel_5.csv",
  header = TRUE,
  skip = 2,
  nrows = 1
) |>
  unlist() |>
  as.numeric()

# Compute cosine similarity
cosine_sim_df <- compute_cosine_similarity(
  signal1 = channel1_data,
  signal2 = channel2_data,
  Fs = 12800,
  window_length = 128,
  overlap_fraction = 0.8,
  preprocess = TRUE
)

```

Next I want to plot the cosine similarity for the 3 metrics, but comparing the first signal of G_6 Test_1 for a particular channel with every signal in G_1 for the same channel number. The same channel in G_6 needs to be compared to the corresponding channel in G_1. The plot should have time (or signal index) on the x axis and cosine similarity on the y axis. The 3 metrics should be visualized in the same plot with different colors. The output will be a plotly plot with one frame for each channel. Please give me the code. Once I get the plotly slide show for the first signal in G_6 Test 1, I would like to repeat for the second signal in G_6 Test 1 and so on. There are 5 signals in G_6 Test 1, so I will have 5 plotly slide shows, with each slideshow consisting of the number of frames equivalent to the number of channels in G_1. Please give me the code. (Note that in the future, I will be comparing signals from G_6 Test 2 with G_1, so please make the code flexible enough to handle that as well. I will also compare G_6 to G_2 and so on later on, so please make the code flexible. For now, I just need the code to compare G_6 Test_1 to G_1). Ask me questions if something isn't clear in the instruction.


```{r}
create_cosine_similarity_viewer <- function(
  test_gearbox = "G_6",
  test_set = "test_1",
  train_gearbox = "G_1",
  base_path = "C:/Users/shish/Documents/rul_challenge_data",
  Fs = 12800,
  window_length = 128,
  overlap_fraction = 0.8,
  preprocess = TRUE,
  test_signal_indices = NULL,
  top_n = NULL # New argument: NULL means plot all points, or specify number like 10
) {
  # Construct paths
  test_path <- file.path(base_path, "test", test_gearbox, test_set)
  train_path <- file.path(base_path, "train", train_gearbox)

  # Get list of channel files in train gearbox
  train_channel_files <- list.files(
    train_path,
    pattern = "^channel_\\d+\\.csv$",
    full.names = FALSE
  )

  if (length(train_channel_files) == 0) {
    stop("No channel files found in ", train_path)
  }

  # Extract channel numbers
  channel_numbers <- as.numeric(
    gsub("channel_(\\d+)\\.csv", "\\1", train_channel_files)
  )
  channel_numbers <- sort(channel_numbers)

  cat(
    "Found",
    length(channel_numbers),
    "channels:",
    paste(channel_numbers, collapse = ", "),
    "\n"
  )

  # Get number of signals in test set
  test_channel_1_path <- file.path(
    test_path,
    paste0("channel_", channel_numbers[1], ".csv")
  )
  test_channel_1_data <- fread(test_channel_1_path, header = TRUE)
  n_test_signals_total <- nrow(test_channel_1_data)

  # Determine which test signals to process
  if (is.null(test_signal_indices)) {
    test_signal_indices <- 1:n_test_signals_total
  } else {
    # Validate indices
    if (
      any(test_signal_indices < 1 | test_signal_indices > n_test_signals_total)
    ) {
      stop("test_signal_indices must be between 1 and ", n_test_signals_total)
    }
  }

  cat("Total signals available:", n_test_signals_total, "\n")
  cat(
    "Processing",
    length(test_signal_indices),
    "signals:",
    paste(test_signal_indices, collapse = ", "),
    "\n"
  )

  if (!is.null(top_n)) {
    cat(
      "Displaying top",
      top_n,
      "highest cosine similarity points per metric\n"
    )
  }

  # Create a list to store all plotly objects (one for each test signal)
  all_plots <- list()

  # Process each test signal
  for (idx in seq_along(test_signal_indices)) {
    test_signal_idx <- test_signal_indices[idx]

    cat(
      "\n=== Processing Test Signal",
      test_signal_idx,
      "(",
      idx,
      "of",
      length(test_signal_indices),
      ") ===\n"
    )

    all_similarity_data <- data.frame()

    # Process each channel
    for (ch_num in channel_numbers) {
      cat("  Channel", ch_num, "...\n")

      # Load test signal for this channel
      test_channel_path <- file.path(
        test_path,
        paste0("channel_", ch_num, ".csv")
      )
      test_channel_data <- fread(test_channel_path, header = TRUE)
      test_signal <- test_channel_data[test_signal_idx, ] |>
        unlist() |>
        as.numeric()

      # Load train data for this channel
      train_channel_path <- file.path(
        train_path,
        paste0("channel_", ch_num, ".csv")
      )
      train_channel_data <- fread(train_channel_path, header = TRUE)
      n_train_signals <- nrow(train_channel_data)

      # Calculate cosine similarity with each train signal
      for (train_signal_idx in 1:n_train_signals) {
        train_signal <- train_channel_data[train_signal_idx, ] |>
          unlist() |>
          as.numeric()

        # Compute cosine similarity
        cos_sim_df <- compute_cosine_similarity(
          signal1 = test_signal,
          signal2 = train_signal,
          Fs = Fs,
          window_length = window_length,
          overlap_fraction = overlap_fraction,
          preprocess = preprocess
        )

        # Add metadata
        cos_sim_df$Channel <- as.factor(ch_num)
        cos_sim_df$Train_Signal_Index <- train_signal_idx

        all_similarity_data <- rbind(all_similarity_data, cos_sim_df)
      }

      if (ch_num %% 2 == 0) {
        cat("    Processed channel", ch_num, "\n")
      }
    }

    # Filter to top N points per metric and channel if requested
    if (!is.null(top_n)) {
      all_similarity_data <- all_similarity_data |>
        group_by(Channel, Metric) |>
        slice_max(order_by = Cosine_Similarity, n = top_n, with_ties = FALSE) |>
        ungroup()
    }

    # Convert Channel to factor with proper ordering
    channel_levels <- as.character(sort(channel_numbers))
    all_similarity_data$Channel <- factor(
      all_similarity_data$Channel,
      levels = channel_levels
    )

    # Create plot title
    plot_title <- paste0(
      "Cosine Similarity: ",
      test_gearbox,
      " ",
      test_set,
      " Signal ",
      test_signal_idx,
      " vs ",
      train_gearbox
    )

    if (!is.null(top_n)) {
      plot_title <- paste0(plot_title, " (Top ", top_n, " per metric)")
    }

    # Create plotly figure with frames for each channel
    fig <- plot_ly(
      all_similarity_data,
      x = ~Train_Signal_Index,
      y = ~Cosine_Similarity,
      color = ~Metric,
      frame = ~Channel,
      type = 'scatter',
      mode = 'markers',
      marker = list(size = 8)
    ) |>
      layout(
        title = plot_title,
        xaxis = list(
          title = paste(train_gearbox, "Signal Index")
        ),
        yaxis = list(
          title = "Cosine Similarity",
          range = c(-1, 1)
        )
      ) |>
      animation_opts(
        frame = 500,
        transition = 300,
        redraw = TRUE
      ) |>
      animation_slider(
        currentvalue = list(
          prefix = "Channel: ",
          visible = TRUE
        )
      ) |>
      animation_button(
        x = 0.1,
        y = 1.1
      )

    all_plots[[idx]] <- fig
    cat("Completed Test Signal", test_signal_idx, "\n")
  }

  # Name the list elements with the actual signal indices
  names(all_plots) <- paste0("signal_", test_signal_indices)

  return(all_plots)
}
```


Usage example:


```{r}
# Compare G_6 Test_1 with G_1
plots_g6_test1_vs_g1_signal1 <- create_cosine_similarity_viewer(
  test_gearbox = "G_6",
  test_set = "test_1",
  train_gearbox = "G_1",
  base_path = "C:/Users/shish/Documents/rul_challenge_data",
  window_length = 128,
  preprocess = TRUE,
  test_signal_indices = 1,
  top_n = 10 # Display top 10 highest cosine similarity points per metric
)

# Display individual plots
plots_g6_test1_vs_g1_signal1[[1]] # First test signal

saveRDS(plots_g6_test1_vs_g1_signal1, "plots_g6_test1_vs_g1_signal1.rds")

plots_g6_test1_vs_g1[[2]] # Second test signal
plots_g6_test1_vs_g1[[3]] # Third test signal
plots_g6_test1_vs_g1[[4]] # Fourth test signal
plots_g6_test1_vs_g1[[5]] # Fifth test signal

# Save all plots
for (i in 1:length(plots_g6_test1_vs_g1)) {
  htmlwidgets::saveWidget(
    plots_g6_test1_vs_g1[[i]],
    paste0("cosine_similarity_G6_test1_signal", i, "_vs_G1.html"),
    selfcontained = TRUE
  )
}
```

Multi stage comparison approach: Coarse to fine strategy.

Stage 1: Ultra-Fast Spectral Fingerprinting (Your idea + improvements)

```{r}
# Extract lightweight spectral fingerprint
extract_spectral_fingerprint <- function(
  signal,
  Fs = 12800,
  preprocess = TRUE
) {
  if (preprocess) {
    signal <- preprocess_signal(signal)
  }

  # Compute FFT
  n <- length(signal)
  fft_result <- fft(signal)
  magnitude <- Mod(fft_result[1:(n / 2)])
  freqs <- (0:(n / 2 - 1)) * Fs / n

  # Focus on fault-relevant range (500-5500 Hz for gear defects)
  freq_mask <- freqs >= 500 & freqs <= 5500
  magnitude_filtered <- magnitude[freq_mask]
  freqs_filtered <- freqs[freq_mask]

  # 1. Spectral Centroid
  spectral_centroid <- sum(freqs_filtered * magnitude_filtered) /
    sum(magnitude_filtered)

  # 2. Top 5 peak frequencies
  peak_indices <- order(magnitude_filtered, decreasing = TRUE)[1:5]
  top_5_freqs <- sort(freqs_filtered[peak_indices])

  # 3. Spectral Spread (variance around centroid)
  spectral_spread <- sqrt(
    sum(((freqs_filtered - spectral_centroid)^2) * magnitude_filtered) /
      sum(magnitude_filtered)
  )

  # 4. Spectral Rolloff (frequency below which 85% of energy is contained)
  cumsum_energy <- cumsum(magnitude_filtered^2)
  total_energy <- sum(magnitude_filtered^2)
  rolloff_idx <- which(cumsum_energy >= 0.85 * total_energy)[1]
  spectral_rolloff <- freqs_filtered[rolloff_idx]

  # 5. RMS (overall energy - very fast to compute)
  rms <- sqrt(mean(signal^2))

  return(c(
    Spectral_Centroid = spectral_centroid,
    Top_Freq_1 = top_5_freqs[1],
    Top_Freq_2 = top_5_freqs[2],
    Top_Freq_3 = top_5_freqs[3],
    Top_Freq_4 = top_5_freqs[4],
    Top_Freq_5 = top_5_freqs[5],
    Spectral_Spread = spectral_spread,
    Spectral_Rolloff = spectral_rolloff,
    RMS = rms
  ))
}

# Pre-compute fingerprints for all signals (multi-channel average)
precompute_spectral_fingerprints <- function(
  gearbox_path,
  channels = 1:11,
  gearbox_name = "Gearbox"
) {
  cat("=== Computing spectral fingerprints for", gearbox_name, "===\n")

  channel_1_data <- fread(
    file.path(gearbox_path, "channel_1.csv"),
    header = TRUE
  )
  n_signals <- nrow(channel_1_data)

  fingerprints_matrix <- matrix(nrow = n_signals, ncol = 9)
  colnames(fingerprints_matrix) <- c(
    "Spectral_Centroid",
    "Top_Freq_1",
    "Top_Freq_2",
    "Top_Freq_3",
    "Top_Freq_4",
    "Top_Freq_5",
    "Spectral_Spread",
    "Spectral_Rolloff",
    "RMS"
  )

  for (signal_idx in 1:n_signals) {
    # Average fingerprint across all channels (or use specific channels)
    channel_fingerprints <- matrix(nrow = length(channels), ncol = 9)

    for (i in seq_along(channels)) {
      ch <- channels[i]
      channel_data <- fread(
        file.path(gearbox_path, paste0("channel_", ch, ".csv")),
        header = TRUE
      )
      signal <- channel_data[signal_idx, ] |> unlist() |> as.numeric()
      channel_fingerprints[i, ] <- extract_spectral_fingerprint(signal)
    }

    # Average across channels (or use weighted average emphasizing vibration channels)
    fingerprints_matrix[signal_idx, ] <- colMeans(
      channel_fingerprints,
      na.rm = TRUE
    )

    if (signal_idx %% 100 == 0) {
      cat("  Processed", signal_idx, "of", n_signals, "\n")
    }
  }

  rownames(fingerprints_matrix) <- paste0("Signal_", 1:n_signals)
  cat("Fingerprint extraction complete!\n\n")

  return(fingerprints_matrix)
}

# Fast fingerprint-based similarity (for 5-signal trajectory)
compute_fingerprint_similarity <- function(
  test_fingerprints,
  train_fingerprints
) {
  # Normalize both
  test_norm <- scale(test_fingerprints)
  train_norm <- scale(train_fingerprints)

  # Flatten and compute cosine similarity
  test_vec <- as.vector(t(test_norm))
  train_vec <- as.vector(t(train_norm))

  # Remove NAs
  valid_idx <- !is.na(test_vec) & !is.na(train_vec)

  cosine_sim <- sum(test_vec[valid_idx] * train_vec[valid_idx]) /
    (sqrt(sum(test_vec[valid_idx]^2)) * sqrt(sum(train_vec[valid_idx]^2)))

  return(cosine_sim)
}
```

Stage 2: Candidate Selection

```{r}
# Fast screening to get top N candidates
fast_candidate_selection <- function(
  test_gearbox_path,
  train_gearbox_path,
  test_signal_indices = 1:5,
  top_n_candidates = 50,
  channels = 1:11
) {
  cat("=== Stage 1: Fast Spectral Fingerprint Screening ===\n")

  # Compute fingerprints
  test_fingerprints_all <- precompute_spectral_fingerprints(
    test_gearbox_path,
    channels,
    "Test"
  )
  train_fingerprints_all <- precompute_spectral_fingerprints(
    train_gearbox_path,
    channels,
    "Train"
  )

  # Extract test trajectory
  test_trajectory <- test_fingerprints_all[test_signal_indices, ]

  n_train <- nrow(train_fingerprints_all)
  window_size <- length(test_signal_indices)
  n_windows <- n_train - window_size + 1

  cat("Screening", n_windows, "windows...\n")

  similarities <- numeric(n_windows)

  for (i in 1:n_windows) {
    train_window <- train_fingerprints_all[i:(i + window_size - 1), ]
    similarities[i] <- compute_fingerprint_similarity(
      test_trajectory,
      train_window
    )
  }

  # Get top N candidates
  top_indices <- order(similarities, decreasing = TRUE)[1:top_n_candidates]

  candidates <- data.frame(
    Window_Start = top_indices,
    Window_End = top_indices + window_size - 1,
    Fingerprint_Similarity = similarities[top_indices]
  )

  cat("\nTop", top_n_candidates, "candidates selected\n")
  cat(
    "Similarity range:",
    round(min(candidates$Fingerprint_Similarity), 3),
    "to",
    round(max(candidates$Fingerprint_Similarity), 3),
    "\n\n"
  )

  return(list(
    candidates = candidates,
    test_fingerprints = test_fingerprints_all,
    train_fingerprints = train_fingerprints_all
  ))
}
```

Stage 3: Refined Full-Feature Comparison

```{r}
# Refine only the top candidates with full features
refine_candidates_with_full_features <- function(
  test_gearbox_path,
  train_gearbox_path,
  candidates,
  test_signal_indices = 1:5,
  test_features = NULL,
  train_features = NULL,
  channels = 1:11,
  preprocess = TRUE
) {
  cat("=== Stage 2: Full Feature Comparison on Top Candidates ===\n")

  # Pre-compute full features if not provided
  if (is.null(test_features)) {
    test_features <- precompute_all_features(
      test_gearbox_path,
      channels,
      preprocess,
      "Test"
    )
  }

  if (is.null(train_features)) {
    train_features <- precompute_all_features(
      train_gearbox_path,
      channels,
      preprocess,
      "Train"
    )
  }

  # Extract test trajectory
  test_trajectory <- extract_trajectory_from_precomputed(
    test_features,
    test_signal_indices
  )

  # Refine only the candidates
  refined_results <- data.frame(
    Window_Start = integer(),
    Window_End = integer(),
    Fingerprint_Similarity = numeric(),
    Mean_Correlation = numeric(),
    Euclidean_Distance = numeric(),
    Cosine_Similarity = numeric()
  )

  for (i in 1:nrow(candidates)) {
    start_idx <- candidates$Window_Start[i]
    end_idx <- candidates$Window_End[i]
    window_indices <- start_idx:end_idx

    train_window <- extract_trajectory_from_precomputed(
      train_features,
      window_indices
    )

    similarity <- compare_trajectories(test_trajectory, train_window)

    refined_results <- rbind(
      refined_results,
      data.frame(
        Window_Start = start_idx,
        Window_End = end_idx,
        Fingerprint_Similarity = candidates$Fingerprint_Similarity[i],
        Mean_Correlation = similarity$mean_correlation,
        Euclidean_Distance = similarity$euclidean_distance,
        Cosine_Similarity = similarity$cosine_similarity
      )
    )

    if (i %% 10 == 0) {
      cat("  Refined", i, "of", nrow(candidates), "candidates\n")
    }
  }

  # Compute composite score
  refined_results$Euclidean_Distance_Norm <- 1 -
    (refined_results$Euclidean_Distance -
      min(refined_results$Euclidean_Distance)) /
      (max(refined_results$Euclidean_Distance) -
        min(refined_results$Euclidean_Distance))

  refined_results$Composite_Score <- (refined_results$Mean_Correlation +
    refined_results$Cosine_Similarity +
    refined_results$Euclidean_Distance_Norm) /
    3

  # Sort by composite score
  refined_results <- refined_results |> arrange(desc(Composite_Score))

  cat("\n=== Refinement Complete ===\n")

  return(refined_results)
}
```

Complete pipeline

```{r}
# Full two-stage pipeline
find_degradation_stage_fast <- function(
  test_gearbox = "G_6",
  test_set = "test_1",
  test_signal_indices = 1:5,
  train_gearbox = "G_1",
  base_path = "C:/Users/shish/Documents/rul_challenge_data",
  channels = 1:11,
  top_n_candidates = 50,
  preprocess = TRUE
) {
  test_path <- file.path(base_path, "test", test_gearbox, test_set)
  train_path <- file.path(base_path, "train", train_gearbox)

  # Stage 1: Fast screening
  stage1_output <- fast_candidate_selection(
    test_path,
    train_path,
    test_signal_indices,
    top_n_candidates,
    channels
  )

  # Stage 2: Refined comparison
  final_results <- refine_candidates_with_full_features(
    test_path,
    train_path,
    stage1_output$candidates,
    test_signal_indices,
    channels = channels,
    preprocess = preprocess
  )

  return(list(
    results = final_results,
    stage1_output = stage1_output
  ))
}
```

Usage:

```{r}
# Run the fast two-stage analysis
output_fast <- find_degradation_stage_fast(
  test_gearbox = "G_6",
  test_set = "test_1",
  test_signal_indices = 1:5,
  train_gearbox = "G_1",
  top_n_candidates = 50, # Screen down from 1433 to 50
  channels = 1:11
)

# View results
head(output_fast$results, 10)

# Visualize
fig_fast <- plot_degradation_matching(output_fast$results, "G_1")
fig_fast
```


The next 2 chnunks take too long. So I abandoned this approach.


Instead of comparing 1 signal at a time and 1 channel at a time, we are going to compare all 5 signals and all channels at once.

My Recommendation: (Claude)
Start with time-domain feature comparison - it's simpler and often more interpretable for degradation
Use multi-channel fusion - don't treat channels independently
Focus on trend matching with your 5 consecutive signals rather than individual signal matching


```{r}
# 1. Pre-compute and store all features for a gearbox
precompute_all_features <- function(
  gearbox_path,
  channels = 1:11,
  preprocess = TRUE,
  gearbox_name = "Gearbox"
) {
  cat("=== Pre-computing features for", gearbox_name, "===\n")

  # Get number of signals from first channel
  channel_1_path <- file.path(gearbox_path, "channel_1.csv")
  channel_1_data <- fread(channel_1_path, header = TRUE)
  n_signals <- nrow(channel_1_data)

  cat("Total signals:", n_signals, "\n")
  cat("Channels:", length(channels), "\n")

  # Initialize storage - will be a matrix with one row per signal
  # Columns will be all features across all channels
  all_features_matrix <- NULL
  feature_names <- NULL

  # Process each signal once
  for (signal_idx in 1:n_signals) {
    signal_features <- list()

    # Extract features from all channels for this signal
    for (ch in channels) {
      channel_path <- file.path(gearbox_path, paste0("channel_", ch, ".csv"))
      channel_data <- fread(channel_path, header = TRUE)
      signal <- channel_data[signal_idx, ] |> unlist() |> as.numeric()

      if (preprocess) {
        signal <- preprocess_signal(signal)
      }

      # Time-domain features
      td_features <- calculate_vibration_timeDomainFeatures(signal)

      # Frequency-domain features (spectral kurtosis summary)
      w_len <- 128
      o_len <- 0.8 * w_len

      spec_output <- specgram(
        signal,
        n = 512,
        Fs = 12800,
        overlap = o_len,
        window = hanning(w_len)
      )

      P_matrix <- Mod(spec_output$S)^2
      freq_bins <- spec_output$f

      # Exclude DC bin
      P_data <- P_matrix[-1, ]
      freq_data <- freq_bins[-1]

      # Calculate SK for frequency range 500-5500 Hz
      freq_mask <- freq_data >= 500 & freq_data <= 5500

      if (sum(freq_mask) > 0) {
        P_data_filtered <- P_data[freq_mask, ]

        # Calculate SK for each frequency bin
        num_freq_bins <- nrow(P_data_filtered)
        sk_values <- numeric(num_freq_bins)

        for (i in 1:num_freq_bins) {
          energy_envelope <- P_data_filtered[i, ]
          sk_values[i] <- e1071::kurtosis(energy_envelope, type = 1) + 1
        }

        # SK summary features
        sk_mean <- mean(sk_values, na.rm = TRUE)
        sk_max <- max(sk_values, na.rm = TRUE)
        sk_std <- sd(sk_values, na.rm = TRUE)
      } else {
        sk_mean <- NA
        sk_max <- NA
        sk_std <- NA
      }

      # Combine all features for this channel
      channel_features <- c(
        unlist(td_features),
        SK_Mean = sk_mean,
        SK_Max = sk_max,
        SK_Std = sk_std
      )

      # Add channel prefix to feature names
      names(channel_features) <- paste0("Ch", ch, ".", names(channel_features))
      signal_features[[ch]] <- channel_features
    }

    # Flatten features for this signal
    signal_feature_vector <- unlist(signal_features)

    # Initialize matrix on first signal
    if (is.null(all_features_matrix)) {
      n_features <- length(signal_feature_vector)
      all_features_matrix <- matrix(nrow = n_signals, ncol = n_features)
      feature_names <- names(signal_feature_vector)
      colnames(all_features_matrix) <- feature_names
    }

    all_features_matrix[signal_idx, ] <- signal_feature_vector

    # Progress indicator
    if (signal_idx %% 50 == 0) {
      cat("  Processed signal", signal_idx, "of", n_signals, "\n")
    }
  }

  rownames(all_features_matrix) <- paste0("Signal_", 1:n_signals)

  cat("Feature extraction complete!\n")
  cat(
    "Matrix dimensions:",
    nrow(all_features_matrix),
    "signals x",
    ncol(all_features_matrix),
    "features\n\n"
  )

  return(all_features_matrix)
}

# 2. Extract trajectory from pre-computed features
extract_trajectory_from_precomputed <- function(
  features_matrix,
  signal_indices
) {
  return(features_matrix[signal_indices, , drop = FALSE])
}

# 3. Compare two feature trajectories (same as before)
compare_trajectories <- function(trajectory1, trajectory2) {
  # Ensure same number of time points
  if (nrow(trajectory1) != nrow(trajectory2)) {
    stop("Trajectories must have the same number of time points")
  }

  if (ncol(trajectory1) != ncol(trajectory2)) {
    stop("Trajectories must have the same features")
  }

  n_timepoints <- nrow(trajectory1)
  n_features <- ncol(trajectory1)

  # Method 1: Correlation of feature trends
  correlations <- numeric(n_features)
  for (i in 1:n_features) {
    correlations[i] <- cor(
      trajectory1[, i],
      trajectory2[, i],
      use = "complete.obs"
    )
  }
  mean_correlation <- mean(correlations, na.rm = TRUE)

  # Method 2: Euclidean distance between normalized trajectories
  # Normalize each trajectory
  traj1_norm <- scale(trajectory1)
  traj2_norm <- scale(trajectory2)
  euclidean_dist <- sqrt(sum((traj1_norm - traj2_norm)^2, na.rm = TRUE))

  # Method 3: Cosine similarity of flattened trajectories
  vec1 <- as.vector(t(traj1_norm))
  vec2 <- as.vector(t(traj2_norm))
  valid_idx <- !is.na(vec1) & !is.na(vec2)
  cosine_sim <- sum(vec1[valid_idx] * vec2[valid_idx]) /
    (sqrt(sum(vec1[valid_idx]^2)) * sqrt(sum(vec2[valid_idx]^2)))

  return(list(
    mean_correlation = mean_correlation,
    euclidean_distance = euclidean_dist,
    cosine_similarity = cosine_sim
  ))
}

# 4. Optimized main function
find_degradation_stage_optimized <- function(
  test_gearbox = "G_6",
  test_set = "test_1",
  test_signal_indices = 1:5,
  train_gearbox = "G_1",
  base_path = "C:/Users/shish/Documents/rul_challenge_data",
  channels = 1:11,
  preprocess = TRUE,
  test_features = NULL, # Optional: pass pre-computed test features
  train_features = NULL # Optional: pass pre-computed train features
) {
  # Paths
  test_path <- file.path(base_path, "test", test_gearbox, test_set)
  train_path <- file.path(base_path, "train", train_gearbox)

  # Pre-compute test features if not provided
  if (is.null(test_features)) {
    test_features <- precompute_all_features(
      gearbox_path = test_path,
      channels = channels,
      preprocess = preprocess,
      gearbox_name = paste(test_gearbox, test_set)
    )
  }

  # Pre-compute train features if not provided
  if (is.null(train_features)) {
    train_features <- precompute_all_features(
      gearbox_path = train_path,
      channels = channels,
      preprocess = preprocess,
      gearbox_name = train_gearbox
    )
  }

  cat("=== Extracting Test Trajectory ===\n")
  test_trajectory <- extract_trajectory_from_precomputed(
    test_features,
    test_signal_indices
  )

  n_train_signals <- nrow(train_features)
  window_size <- length(test_signal_indices)

  cat("\n=== Comparing with", train_gearbox, "===\n")
  cat("Window size:", window_size, "\n")
  cat("Number of windows to test:", n_train_signals - window_size + 1, "\n\n")

  # Storage for similarity scores
  results <- data.frame(
    Window_Start = integer(),
    Window_End = integer(),
    Mean_Correlation = numeric(),
    Euclidean_Distance = numeric(),
    Cosine_Similarity = numeric()
  )

  # Slide window through train data
  for (start_idx in 1:(n_train_signals - window_size + 1)) {
    end_idx <- start_idx + window_size - 1
    window_indices <- start_idx:end_idx

    # Extract train window trajectory (instant - no re-computation!)
    train_window_trajectory <- extract_trajectory_from_precomputed(
      train_features,
      window_indices
    )

    # Compare trajectories
    similarity <- compare_trajectories(test_trajectory, train_window_trajectory)

    results <- rbind(
      results,
      data.frame(
        Window_Start = start_idx,
        Window_End = end_idx,
        Mean_Correlation = similarity$mean_correlation,
        Euclidean_Distance = similarity$euclidean_distance,
        Cosine_Similarity = similarity$cosine_similarity
      )
    )

    if (start_idx %% 100 == 0) {
      cat(
        "Processed window",
        start_idx,
        "of",
        n_train_signals - window_size + 1,
        "\n"
      )
    }
  }

  cat("\n=== Analysis Complete ===\n")

  # Create composite score (normalize and combine metrics)
  results$Euclidean_Distance_Norm <- 1 -
    (results$Euclidean_Distance - min(results$Euclidean_Distance)) /
      (max(results$Euclidean_Distance) - min(results$Euclidean_Distance))

  results$Composite_Score <- (results$Mean_Correlation +
    results$Cosine_Similarity +
    results$Euclidean_Distance_Norm) /
    3

  # Return results along with pre-computed features for reuse
  return(list(
    results = results,
    test_features = test_features,
    train_features = train_features
  ))
}

# 5. Visualization function (same as before)
plot_degradation_matching <- function(results, train_gearbox = "G_1") {
  # Find best matches
  best_correlation <- results[which.max(results$Mean_Correlation), ]
  best_cosine <- results[which.max(results$Cosine_Similarity), ]
  best_euclidean <- results[which.min(results$Euclidean_Distance), ]
  best_composite <- results[which.max(results$Composite_Score), ]

  # Create interactive plot
  fig <- plot_ly(results, x = ~Window_Start) |>
    add_trace(
      y = ~Mean_Correlation,
      name = "Mean Correlation",
      type = 'scatter',
      mode = 'lines+markers',
      line = list(width = 2)
    ) |>
    add_trace(
      y = ~Cosine_Similarity,
      name = "Cosine Similarity",
      type = 'scatter',
      mode = 'lines+markers',
      line = list(width = 2)
    ) |>
    add_trace(
      y = ~Euclidean_Distance_Norm,
      name = "Euclidean (Normalized)",
      type = 'scatter',
      mode = 'lines+markers',
      line = list(width = 2)
    ) |>
    add_trace(
      y = ~Composite_Score,
      name = "Composite Score",
      type = 'scatter',
      mode = 'lines+markers',
      line = list(width = 2, dash = 'dash')
    ) |>
    layout(
      title = paste("G_6 Degradation Stage Matching with", train_gearbox),
      xaxis = list(title = paste(train_gearbox, "Signal Window Start Index")),
      yaxis = list(title = "Similarity Score", range = c(0, 1)),
      hovermode = "x unified"
    )

  # Print summary
  cat("\n=== Best Matches ===\n")
  cat(
    "By Mean Correlation:",
    best_correlation$Window_Start,
    "-",
    best_correlation$Window_End,
    "(score:",
    round(best_correlation$Mean_Correlation, 3),
    ")\n"
  )
  cat(
    "By Cosine Similarity:",
    best_cosine$Window_Start,
    "-",
    best_cosine$Window_End,
    "(score:",
    round(best_cosine$Cosine_Similarity, 3),
    ")\n"
  )
  cat(
    "By Euclidean Distance:",
    best_euclidean$Window_Start,
    "-",
    best_euclidean$Window_End,
    "(score:",
    round(best_euclidean$Euclidean_Distance, 2),
    ")\n"
  )
  cat(
    "By Composite Score:",
    best_composite$Window_Start,
    "-",
    best_composite$Window_End,
    "(score:",
    round(best_composite$Composite_Score, 3),
    ")\n"
  )

  return(fig)
}
```

Next, run the analysis.


```{r}
# # Option 1: Let the function pre-compute features automatically
# output <- find_degradation_stage_optimized(
#   test_gearbox = "G_6",
#   test_set = "test_1",
#   test_signal_indices = 1:5,
#   train_gearbox = "G_1",
#   base_path = "C:/Users/shish/Documents/rul_challenge_data",
#   channels = 1:11,
#   preprocess = TRUE
# )

# results <- output$results
# fig <- plot_degradation_matching(results, train_gearbox = "G_1")
# fig

# # Save results and plot
# saveRDS(output, "g6_test1_vs_g1_output.rds")
# htmlwidgets::saveWidget(fig, "g6_test1_vs_g1_matching.html", selfcontained = TRUE)

# # View top matches
# top_matches <- results |>
#   arrange(desc(Composite_Score)) |>
#   head(10)
# top_matches

# Option 2: Pre-compute once, reuse many times (RECOMMENDED for multiple analyses)
# Pre-compute G_6 test_1 features once
g6_test1_features <- precompute_all_features(
  gearbox_path = "C:/Users/shish/Documents/rul_challenge_data/test/G_6/test_1",
  channels = 1:11,
  preprocess = TRUE,
  gearbox_name = "G_6 Test_1"
)

# Pre-compute G_1 features once
g1_features <- precompute_all_features(
  gearbox_path = "C:/Users/shish/Documents/rul_challenge_data/train/G_1",
  channels = 1:11,
  preprocess = TRUE,
  gearbox_name = "G_1"
)

# Save pre-computed features for future use
saveRDS(g6_test1_features, "g6_test1_features.rds")
saveRDS(g1_features, "g1_features.rds")

# Now run analysis with pre-computed features (much faster!)
output2 <- find_degradation_stage_optimized(
  test_gearbox = "G_6",
  test_set = "test_1",
  test_signal_indices = 1:5,
  train_gearbox = "G_1",
  test_features = g6_test1_features,
  train_features = g1_features
)

results2 <- output2$results
fig2 <- plot_degradation_matching(results2, train_gearbox = "G_1")
fig2

# If you want to compare with G_2 later (reuse G_6 features!)
g2_features <- precompute_all_features(
  gearbox_path = "C:/Users/shish/Documents/rul_challenge_data/train/G_2",
  channels = 1:11,
  preprocess = TRUE,
  gearbox_name = "G_2"
)

output_g2 <- find_degradation_stage_optimized(
  test_gearbox = "G_6",
  test_set = "test_1",
  test_signal_indices = 1:5,
  train_gearbox = "G_2",
  test_features = g6_test1_features, # Reuse!
  train_features = g2_features
)

results_g2 <- output_g2$results
fig_g2 <- plot_degradation_matching(results_g2, train_gearbox = "G_2")
fig_g2

# Compare G_6 test_2 with G_1 (reuse G_1 features!)
g6_test2_features <- precompute_all_features(
  gearbox_path = "C:/Users/shish/Documents/rul_challenge_data/test/G_6/test_2",
  channels = 1:11,
  preprocess = TRUE,
  gearbox_name = "G_6 Test_2"
)

output_test2 <- find_degradation_stage_optimized(
  test_gearbox = "G_6",
  test_set = "test_2",
  test_signal_indices = 1:5,
  train_gearbox = "G_1",
  test_features = g6_test2_features,
  train_features = g1_features # Reuse!
)

results_test2 <- output_test2$results
fig_test2 <- plot_degradation_matching(results_test2, train_gearbox = "G_1")
fig_test2
```

ROUGH


```{r}
# Load 1 signal from G_6 Test_1 Channel 5

test_signal_path <- "C:/Users/shish/Documents/rul_challenge_data/test/G_6/test_1/channel_5.csv"

test_signal_data <- fread(test_signal_path, header = TRUE, skip = 0, nrows = 1) |>
  unlist() |>
  as.numeric()

fft_result <- fft(test_signal_data)
magnitude <- Mod(fft_result)
freqs <- (0:(length(test_signal_data) - 1)) * 12800 / length(test_signal_data)
```